### 2025-02-21 latex/paper.tex
add project files

% This must be in the first 5 lines to tell arXiv to use pdfLaTeX, which is strongly recommended.
\pdfoutput=1
% In particular, the hyperref package requires pdfLaTeX in order to break URLs across lines.

\documentclass[11pt]{article}

% Change "review" to "final" to generate the final (sometimes called camera-ready) version.
% Change to "preprint" to generate a non-anonymous version with page numbers.
\usepackage[review]{acl}
% \usepackage{acl}

% Standard package includes
\usepackage{times}
\usepackage{latexsym}

% For proper rendering and hyphenation of words containing Latin characters (including in bib files)
\usepackage[T1]{fontenc}
% For Vietnamese characters
% \usepackage[T5]{fontenc}
% See https://www.latex-project.org/help/documentation/encguide.pdf for other character sets

% This assumes your files are encoded as UTF8
\usepackage[utf8]{inputenc}

% This is not strictly necessary, and may be commented out,
% but it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}

% This is also not strictly necessary, and may be commented out.
% However, it will improve the aesthetics of text in
% the typewriter font.
\usepackage{inconsolata}

%Including images in your LaTeX document requires adding
%additional package(s)
\usepackage{graphicx}

% If the title and author information does not fit in the area allocated, uncomment the following
%
%\setlength\titlebox{<dim>}
%
% and set <dim> to something 5cm or larger.

\title{YNWA_PZ at SemEval-2025 Task 11: Descriptive Title}

% Author information can be set in various styles:
% For several authors from the same institution:
% \author{Author 1 \and ... \and Author n \\
%         Address line \\ ... \\ Address line}
% if the names do not fit well on one line use
%         Author 1 \\ {\bf Author 2} \\ ... \\ {\bf Author n} \\
% For authors from different institutions:
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \And  ... \And
%         Author n \\ Address line \\ ... \\ Address line}
% To start a separate ``row'' of authors use \AND, as in
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \AND
%         Author 2 \\ Address line \\ ... \\ Address line \And
%         Author 3 \\ Address line \\ ... \\ Address line}

\author{First Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  \texttt{email@domain} \\\And
  Second Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  \texttt{email@domain} \\}

%\author{
%  \textbf{First Author\textsuperscript{1}},
%  \textbf{Second Author\textsuperscript{1,2}},
%  \textbf{Third T. Author\textsuperscript{1}},
%  \textbf{Fourth Author\textsuperscript{1}},
%\\
%  \textbf{Fifth Author\textsuperscript{1,2}},
%  \textbf{Sixth Author\textsuperscript{1}},
%  \textbf{Seventh Author\textsuperscript{1}},
%  \textbf{Eighth Author \textsuperscript{1,2,3,4}},
%\\
%  \textbf{Ninth Author\textsuperscript{1}},
%  \textbf{Tenth Author\textsuperscript{1}},
%  \textbf{Eleventh E. Author\textsuperscript{1,2,3,4,5}},
%  \textbf{Twelfth Author\textsuperscript{1}},
%\\
%  \textbf{Thirteenth Author\textsuperscript{3}},
%  \textbf{Fourteenth F. Author\textsuperscript{2,4}},
%  \textbf{Fifteenth Author\textsuperscript{1}},
%  \textbf{Sixteenth Author\textsuperscript{1}},
%\\
%  \textbf{Seventeenth S. Author\textsuperscript{4,5}},
%  \textbf{Eighteenth Author\textsuperscript{3,4}},
%  \textbf{Nineteenth N. Author\textsuperscript{2,5}},
%  \textbf{Twentieth Author\textsuperscript{1}}
%\\
%\\
%  \textsuperscript{1}Affiliation 1,
%  \textsuperscript{2}Affiliation 2,
%  \textsuperscript{3}Affiliation 3,
%  \textsuperscript{4}Affiliation 4,
%  \textsuperscript{5}Affiliation 5
%\\
%  \small{
%    \textbf{Correspondence:} \href{mailto:email@domain}{email@domain}
%  }
%}

\begin{document}
\maketitle
\begin{abstract}
  This document is a supplement to the general instructions for *ACL authors. It contains instructions for using the \LaTeX{} style files for ACL conferences.
  The document itself conforms to its own specifications, and is therefore an example of what your manuscript should look like.
  These instructions should be used both for papers submitted for review and for final versions of accepted papers.
\end{abstract}

\section{Introduction}

These instructions are for authors submitting papers to *ACL conferences using \LaTeX. They are not self-contained. All authors must follow the general instructions for *ACL proceedings,\footnote{\url{http://acl-org.github.io/ACLPUB/formatting.html}} and this document contains additional instructions for the \LaTeX{} style files.

The templates include the \LaTeX{} source of this document (\texttt{acl\_latex.tex}),
the \LaTeX{} style file used to format it (\texttt{acl.sty}),
an ACL bibliography style (\texttt{acl\_natbib.bst}),
an example bibliography (\texttt{custom.bib}),
and the bibliography for the ACL Anthology (\texttt{anthology.bib}).

\section{Engines}

To produce a PDF file, pdf\LaTeX{} is strongly recommended (over original \LaTeX{} plus dvips+ps2pdf or dvipdf).
The style file \texttt{acl.sty} can also be used with
lua\LaTeX{} and
Xe\LaTeX{}, which are especially suitable for text in non-Latin scripts.
The file \texttt{acl\_lualatex.tex} in this repository provides
an example of how to use \texttt{acl.sty} with either
lua\LaTeX{} or
Xe\LaTeX{}.

\section{Preamble}

The first line of the file must be
\begin{quote}
  \begin{verbatim}
\documentclass[11pt]{article}
\end{verbatim}
\end{quote}

To load the style file in the review version:
\begin{quote}
  \begin{verbatim}
\usepackage[review]{acl}
\end{verbatim}
\end{quote}
For the final version, omit the \verb|review| option:
\begin{quote}
  \begin{verbatim}
\usepackage{acl}
\end{verbatim}
\end{quote}

To use Times Roman, put the following in the preamble:
\begin{quote}
  \begin{verbatim}
\usepackage{times}
\end{verbatim}
\end{quote}
(Alternatives like txfonts or newtx are also acceptable.)

Please see the \LaTeX{} source of this document for comments on other packages that may be useful.

Set the title and author using \verb|\title| and \verb|\author|. Within the author list, format multiple authors using \verb|\and| and \verb|\And| and \verb|\AND|; please see the \LaTeX{} source for examples.

By default, the box containing the title and author names is set to the minimum of 5 cm. If you need more space, include the following in the preamble:
\begin{quote}
  \begin{verbatim}
\setlength\titlebox{<dim>}
\end{verbatim}
\end{quote}
where \verb|<dim>| is replaced with a length. Do not set this length smaller than 5 cm.

\section{Document Body}

\subsection{Footnotes}

Footnotes are inserted with the \verb|\footnote| command.\footnote{This is a footnote.}

\subsection{Tables and figures}

See Table~\ref{tab:accents} for an example of a table and its caption.
\textbf{Do not override the default caption sizes.}

\begin{table}
  \centering
  \begin{tabular}{lc}
    \hline
    \textbf{Command} & \textbf{Output} \\
    \hline
    \verb|{\"a}|     & {\"a}           \\
    \verb|{\^e}|     & {\^e}           \\
    \verb|{\`i}|     & {\`i}           \\
    \verb|{\.I}|     & {\.I}           \\
    \verb|{\o}|      & {\o}            \\
    \verb|{\'u}|     & {\'u}           \\
    \verb|{\aa}|     & {\aa}           \\\hline
  \end{tabular}
  \begin{tabular}{lc}
    \hline
    \textbf{Command} & \textbf{Output} \\
    \hline
    \verb|{\c c}|    & {\c c}          \\
    \verb|{\u g}|    & {\u g}          \\
    \verb|{\l}|      & {\l}            \\
    \verb|{\~n}|     & {\~n}           \\
    \verb|{\H o}|    & {\H o}          \\
    \verb|{\v r}|    & {\v r}          \\
    \verb|{\ss}|     & {\ss}           \\
    \hline
  \end{tabular}
  \caption{Example commands for accented characters, to be used in, \emph{e.g.}, Bib\TeX{} entries.}
  \label{tab:accents}
\end{table}

As much as possible, fonts in figures should conform
to the document fonts. See Figure~\ref{fig:experiments} for an example of a figure and its caption.

Using the \verb|graphicx| package graphics files can be included within figure
environment at an appropriate point within the text.
The \verb|graphicx| package supports various optional arguments to control the
appearance of the figure.
You must include it explicitly in the \LaTeX{} preamble (after the
\verb|\documentclass| declaration and before \verb|\begin{document}|) using
\verb|\usepackage{graphicx}|.

\begin{figure}[t]
  \includegraphics[width=\columnwidth]{example-image-golden}
  \caption{A figure with a caption that runs for more than one line.
    Example image is usually available through the \texttt{mwe} package
    without even mentioning it in the preamble.}
  \label{fig:experiments}
\end{figure}

\begin{figure*}[t]
  \includegraphics[width=0.48\linewidth]{example-image-a} \hfill
  \includegraphics[width=0.48\linewidth]{example-image-b}
  \caption {A minimal working example to demonstrate how to place
    two images side-by-side.}
\end{figure*}

\subsection{Hyperlinks}

Users of older versions of \LaTeX{} may encounter the following error during compilation:
\begin{quote}
  \verb|\pdfendlink| ended up in different nesting level than \verb|\pdfstartlink|.
\end{quote}
This happens when pdf\LaTeX{} is used and a citation splits across a page boundary. The best way to fix this is to upgrade \LaTeX{} to 2018-12-01 or later.

\subsection{Citations}

\begin{table*}
  \centering
  \begin{tabular}{lll}
    \hline
    \textbf{Output}           & \textbf{natbib command} & \textbf{ACL only command} \\
    \hline
    \citep{Gusfield:97}       & \verb|\citep|           &                           \\
    \citealp{Gusfield:97}     & \verb|\citealp|         &                           \\
    \citet{Gusfield:97}       & \verb|\citet|           &                           \\
    \citeyearpar{Gusfield:97} & \verb|\citeyearpar|     &                           \\
    \citeposs{Gusfield:97}    &                         & \verb|\citeposs|          \\
    \hline
  \end{tabular}
  \caption{\label{citation-guide}
    Citation commands supported by the style file.
    The style is based on the natbib package and supports all natbib citation commands.
    It also supports commands defined in previous ACL style files for compatibility.
  }
\end{table*}

Table~\ref{citation-guide} shows the syntax supported by the style files.
We encourage you to use the natbib styles.
You can use the command \verb|\citet| (cite in text) to get ``author (year)'' citations, like this citation to a paper by \citet{Gusfield:97}.
You can use the command \verb|\citep| (cite in parentheses) to get ``(author, year)'' citations \citep{Gusfield:97}.
You can use the command \verb|\citealp| (alternative cite without parentheses) to get ``author, year'' citations, which is useful for using citations within parentheses (e.g. \citealp{Gusfield:97}).

A possessive citation can be made with the command \verb|\citeposs|.
This is not a standard natbib command, so it is generally not compatible
with other style files.

\subsection{References}

\nocite{Ando2005,andrew2007scalable,rasooli-tetrault-2015}

The \LaTeX{} and Bib\TeX{} style files provided roughly follow the American Psychological Association format.
If your own bib file is named \texttt{custom.bib}, then placing the following before any appendices in your \LaTeX{} file will generate the references section for you:
\begin{quote}
  \begin{verbatim}
\bibliography{references}
\end{verbatim}
\end{quote}

You can obtain the complete ACL Anthology as a Bib\TeX{} file from \url{https://aclweb.org/anthology/anthology.bib.gz}.
To include both the Anthology and your own .bib file, use the following instead of the above.
\begin{quote}
  \begin{verbatim}
\bibliography{anthology,custom}
\end{verbatim}
\end{quote}

Please see Section~\ref{sec:bibtex} for information on preparing Bib\TeX{} files.

\subsection{Equations}

An example equation is shown below:
\begin{equation}
  \label{eq:example}
  A = \pi r^2
\end{equation}

Labels for equation numbers, sections, subsections, figures and tables
are all defined with the \verb|\label{label}| command and cross references
to them are made with the \verb|\ref{label}| command.

This an example cross-reference to Equation~\ref{eq:example}.

\subsection{Appendices}

Use \verb|\appendix| before any appendix section to switch the section numbering over to letters. See Appendix~\ref{sec:appendix} for an example.

\section{Bib\TeX{} Files}
\label{sec:bibtex}

Unicode cannot be used in Bib\TeX{} entries, and some ways of typing special characters can disrupt Bib\TeX's alphabetization. The recommended way of typing special characters is shown in Table~\ref{tab:accents}.

Please ensure that Bib\TeX{} records contain DOIs or URLs when possible, and for all the ACL materials that you reference.
Use the \verb|doi| field for DOIs and the \verb|url| field for URLs.
If a Bib\TeX{} entry has a URL or DOI field, the paper title in the references section will appear as a hyperlink to the paper, using the hyperref \LaTeX{} package.

\section*{Limitations}

Since December 2023, a "Limitations" section has been required for all papers submitted to ACL Rolling Review (ARR). This section should be placed at the end of the paper, before the references. The "Limitations" section (along with, optionally, a section for ethical considerations) may be up to one page and will not count toward the final page limit. Note that these files may be used by venues that do not rely on ARR so it is recommended to verify the requirement of a "Limitations" section and other criteria with the venue in question.

\section*{Acknowledgments}

This document has been adapted
by Steven Bethard, Ryan Cotterell and Rui Yan
from the instructions for earlier ACL and NAACL proceedings, including those for
ACL 2019 by Douwe Kiela and Ivan Vuli\'{c},
NAACL 2019 by Stephanie Lukin and Alla Roskovskaya,
ACL 2018 by Shay Cohen, Kevin Gimpel, and Wei Lu,
NAACL 2018 by Margaret Mitchell and Stephanie Lukin,
Bib\TeX{} suggestions for (NA)ACL 2017/2018 from Jason Eisner,
ACL 2017 by Dan Gildea and Min-Yen Kan,
NAACL 2017 by Margaret Mitchell,
ACL 2012 by Maggie Li and Michael White,
ACL 2010 by Jing-Shin Chang and Philipp Koehn,
ACL 2008 by Johanna D. Moore, Simone Teufel, James Allan, and Sadaoki Furui,
ACL 2005 by Hwee Tou Ng and Kemal Oflazer,
ACL 2002 by Eugene Charniak and Dekang Lin,
and earlier ACL and EACL formats written by several people, including
John Chen, Henry S. Thompson and Donald Walker.
Additional elements were taken from the formatting instructions of the \emph{International Joint Conference on Artificial Intelligence} and the \emph{Conference on Computer Vision and Pattern Recognition}.

% Bibliography entries for the entire Anthology, followed by custom entries
%\bibliography{anthology,custom}
% Custom bibliography entries only
\bibliography{references}

\appendix

\section{Example Appendix}
\label{sec:appendix}

This is an appendix.

\end{document}

### 2025-02-21 runs/Untitled-1.py

@@ -1,0 +1,39 @@
+langs=["amh","arq","ary","chn","deu","esp","hau","hin","ibo","kin","mar","orm","pcm","ptbr","ptmz","ron","rus","som","sun","swa","swe","tat","tir","ukr","vmw","yor","ind","jav","xho","zul"]
+langs2country={
+    "afr":"Afrikaans",
+    "amh":"Amharic",
+    "arq":"Algerian Arabic",
+    "ary":"Moroccan Arabic",
+    "chn":"Chinese",
+    "deu":"German",
+    "esp":"Latin American Spanish",
+    "eng":"English",
+    "hau":"Hausa",
+    "hin":"Hindi",
+    "ibo":"Igbo",
+    "kin":"Kinyarwanda",
+    
+    "mar":"Marathi",
+    "orm":"Oromo",
+    "pcm":"Nigerian-Pidgin",
+    "ptbr":"Brazilian Portuguese",
+    "ptmz":"Mozambican Portuguese",
+    "ron":"Romanian",
+    "rus":"Russian",
+    "som":"Somali",
+    "sun":"",#Sundanese
+    "swa":"Swahili",
+    "swe":"Swedish",
+    "tat":"Tatar",
+    "tir":"Tigrinya",
+    "ukr":"Ukrainian",
+    "vmw":"",#Makhuwa
+    "yor":"Yoruba",
+    "ind":"Indonesian",
+    "jav":"Javanese",
+    "xho":"isiXhosa",
+    "zul":"isiZulu Arabic",
+}
+"""
+Setswana, Xitsonga
+"""

### 2025-02-21 paper/sections/SystemOverview.tex
add System Overview section

% \section{System Overview}

% Assume the role of an academic researcher in Computer Science. Your task is to contribute to a collaborative paper by writing a section focused on System Overview of . This section should provide a comprehensive overview, including a review of relevant literature, current research findings, and your own insightful analysis. Ensure your writing is clear, concise, and adheres to the academic standards of your field, including proper citation of sources using \citep{}. Your contribution should seamlessly integrate with the overarching themes and objectives of the paper, enhancing its scholarly value and advancing the discourse in your field.

% we preprocessed the text and for feature extraction we used diffrent models such as LSTM, multilingual Language models and LLMs.we finetuned LLMs using LORA method.
% after extracting the feature vector. we used both approaches using the embedding layer output and last hidden state of the model. we used the classifier to do the classification task such as Multi Layer Perceptron(MLP), XGBoost, Support Vector Machine(SVM) to solve multi label classification.

% mostly we used different combination of these for diffrent languages.
% - Key algorithms and modeling decisions/steps in detail.
% - The resources beyond training data (e.g., lexicons, other data,...).

% - The maths behind your model and its explanation in plain English.
% \section{System Overview}

% Our system for sentiment analysis across multiple languages is built on a series of carefully designed steps, combining preprocessing techniques, feature extraction models, and classification strategies. Below, we present the key components and decisions that shape our approach.

% \subsection{Preprocessing and Feature Extraction}
% The first step in our pipeline involves preprocessing the text data to ensure consistency and compatibility across multiple languages. This includes tasks such as tokenization, lowercasing, removing stopwords (if applicable), and handling special characters.

% For feature extraction, we experimented with a variety of models, including Long Short-Term Memory networks (LSTMs), multilingual language models (e.g., mBERT, XLM-R), and large language models (LLMs) such as GPT-based architectures. These models were chosen for their ability to capture semantic meaning across different languages effectively.

% After generating the feature representations, we explored two primary approaches:
% \begin{itemize}
%     \item Using the embedding layer output directly as feature vectors.
%     \item Leveraging the last hidden state of the model to capture the contextualized representation of the input text.
% \end{itemize}

% \subsection{Classification Step}
% Once the feature vectors were extracted, we focused on solving the multi-label classification problem. We investigated a range of classifiers to determine the most effective approach for this task. The models we used include:
% \begin{itemize}
%     \item \textbf{Multi-Layer Perceptron (MLP):} A neural network-based approach to model complex relationships between features and output labels.
%     \item \textbf{XGBoost:} A gradient boosting framework that performs well on tabular data and can handle multi-label tasks efficiently.
%     \item \textbf{Support Vector Machine (SVM):} A traditional machine learning classifier, which we adapted to handle multi-label outputs.
% \end{itemize}

% By combining these classifiers with the extracted features, we aimed to achieve high performance across different languages and sentiment labels.

% \subsection{Fine-Tuning LLMs with LoRA}
% To further enhance the performance of the large language models (LLMs), we applied the Low-Rank Adaptation (LoRA) fine-tuning method. LoRA allows for efficient fine-tuning by freezing the pre-trained model weights and introducing trainable low-rank matrices. This approach significantly reduces the computational cost of fine-tuning while maintaining strong performance. Using LoRA, we adapted the LLMs to our specific multi-label sentiment analysis task, ensuring that they could better handle the nuances of different languages and sentiment categories.

% \subsection{Mathematical Foundation in Plain English}
% At the core of our system lies the mathematical representation of text data. In simple terms:
% \begin{itemize}
%     \item The text is first converted into numerical representations (vectors) by the feature extraction models. These vectors capture the meaning and context of the words in the text.
%     \item The classifiers then map these vectors to the output labels. For multi-label classification, this means predicting multiple sentiment categories (e.g., positive, negative, neutral) for a single input text. Each label is treated as a binary decision (present or absent), and the model optimizes for all labels simultaneously.
% \end{itemize}

% The fine-tuning process (e.g., LoRA) refines the weights of the models to align better with our specific dataset, ensuring accurate predictions across multiple languages.

% \subsection{Model Variants and Experiments}
% Throughout our experimentation, we tested several variants of the system:
% \begin{itemize}
%     \item \textbf{Feature extraction models:} Comparing LSTMs, multilingual models (like mBERT), and LLMs to determine their effectiveness in capturing cross-lingual sentiment.
%     \item \textbf{Classification approaches:} Evaluating the performance of MLP, XGBoost, and SVM with different feature representations.
%     \item \textbf{Fine-tuning strategies:} Exploring the impact of LoRA versus full fine-tuning on the LLMs.
% \end{itemize}

% By systematically evaluating these variants, we identified the optimal configuration for our multi-label, multi-language sentiment analysis task.
% \section{Methodology}
\section{System Overview}

In this section, we present a comprehensive overview of our system for multi-label text classification, which integrates various deep learning architectures and machine learning classifiers. The system follows a pipeline that includes text preprocessing, feature extraction using neural network models, and classification through different machine learning algorithms.

\subsection{Preprocessing}

The preprocessing pipeline involves multiple steps to clean and standardize the text data. Initially, all text is converted to lowercase and unnecessary whitespace is removed. Then, special characters, URLs, and emojis are filtered out using regular expressions. Each emoji is replaced by its corresponding title (e.g., \smiley → "smiling face"). Tokenization is performed using language-specific tokenizers to ensure optimal segmentation. Finally, stopwords are removed, and text normalization techniques, such as stemming or lemmatization, are applied where appropriate.

\subsection{Feature Extraction}

To extract features, we employed a diverse range of models, including Long Short-Term Memory (LSTM) networks, multilingual language models, and Large Language Models (LLMs). The LLMs were fine-tuned using Low-Rank Adaptation (LoRA) \citep{hu2021lora}, a parameter-efficient tuning method that facilitates task-specific adaptation while maintaining computational efficiency.

The extracted feature vectors were derived using two distinct approaches. The first approach utilized the output from the embedding layer of the models, which captures contextual word representations in a lower-dimensional vector space. The second approach involved extracting the final hidden state of the neural network, which encapsulates high-level semantic information of the text.

\subsection{Classification Approach}

Following feature extraction, we applied multiple classification algorithms to perform the multi-label classification task. One of the classifiers used was the Multi-Layer Perceptron (MLP), a feedforward artificial neural network capable of modeling complex relationships between the extracted features and the target labels. Additionally, the system employed XGBoost, a gradient boosting framework renowned for its effectiveness in structured data classification \citep{chen2016xgboost}. Furthermore, Support Vector Machines (SVMs) were utilized as a classification method due to their ability to operate effectively in high-dimensional feature spaces by identifying optimal hyperplanes for classification \citep{cortes1995support}.

By combining these techniques, the proposed system captures rich linguistic representations of the input text and achieves accurate multi-label classification. The experimental setup and evaluation metrics used to validate the effectiveness of this approach are discussed in subsequent sections.

### 2025-02-21 paper/sections/introduction.tex
add Introduction section

\section{Introduction}
The analysis and processing of emotions from textual data have become crucial in understanding human communication across different languages and cultures. This study focuses on the detection and classification of emotions across diverse linguistic contexts, spanning regions from South America to East Asia. Our objective is to categorize emotions into key dimensions, namely sadness, anger, fear, joy, and surprise, while considering cross-lingual variations and linguistic complexities.

To address these challenges, we structure our study into three distinct tracks: (1) Track A involves binary emotion classification, determining whether a given text expresses a particular emotion; (2) Track B measures the intensity of emotions on a scale from 0 to 3, enabling a more granular understanding of emotional expressions; and (3) Track C explores cross-lingual emotion detection, facilitating insights into emotional patterns across different languages.

Understanding emotions based on textual data plays a pivotal role in various applications, including social media analysis, behavioral research, and the study of emotions' influence on social interactions. Our work contributes to the development of robust emotion recognition systems, enabling better comprehension of multilingual emotional expressions and their implications in computational linguistics.

Despite the significant advancements in emotion classification, several challenges persist. Some languages exhibit highly complex grammatical structures, making it difficult to train effective models. Additionally, the classification of emotions in low-resource languages is hindered by data scarcity and syntactic intricacies. Furthermore, certain machine learning models demonstrate suboptimal performance when applied to multilingual emotion classification, necessitating the development of novel techniques to enhance model adaptability and generalization.

To address these limitations, we present a comprehensive analysis of state-of-the-art methodologies and evaluate their effectiveness across multiple languages. Our findings highlight the critical role of language-specific preprocessing techniques, domain adaptation strategies, and transfer learning in improving multilingual emotion classification.

All code implementations, including the models and experimental setups employed in this study, are publicly available on GitHub:\footnote{\url{https://github.com/YNWA-PZ/SemEval2025-task11}}. This repository provides full documentation of our methodologies, experimental results, and final model architectures.

### 2025-02-21 paper/sections/ExperimentalSetup.tex
add Experimental Setup section

\section{Experimental Setup}

This section describes the experimental setup, providing details about data splits, preprocessing steps, hyperparameter tuning, and the tools and libraries utilized. The goal is to ensure reproducibility, transparency, and alignment with established best practices in machine learning research.

\subsection{Data Splits and Usage}

The dataset was divided into three subsets: training, development (validation), and testing. Specifically, 80\% of the training dataset was allocated for training, while the remaining 20\% was reserved for validation to facilitate model selection. Once the best-performing model was identified during the validation phase, the entire training and development datasets were combined to retrain the final model. This final model was then evaluated on the test dataset, which was held out during the entire training process to ensure an unbiased assessment of the model's generalization performance. This approach adheres to standard practices in machine learning research to prevent data leakage and ensure robust evaluation \citep{Goodfellow-et-al-2016}.

\subsection{Preprocessing}

Preprocessing of the dataset was performed using the \texttt{clean-text} library. The preprocessing pipeline included standardizing the text by lowercasing all characters, removing special characters and punctuation, and normalizing tokens through contraction expansion and the elimination of redundant whitespace. These steps ensured the data was clean and consistent across all subsets. Details of the preprocessing pipeline are provided in the supplementary material (Appendix A). Preprocessing was applied consistently to the training, validation, and test datasets to avoid introducing biases or inconsistencies. Such preprocessing steps have been shown to improve the performance of natural language processing (NLP) models by reducing noise and simplifying the input representations \citep{Zhang2020DataPrep}.

\subsection{Hyperparameter Tuning}

Hyperparameter tuning was conducted using \texttt{Optuna}, an advanced framework for automated hyperparameter optimization \citep{Akiba2019Optuna}. The hyperparameters tuned included the learning rate, batch size, dropout rate, and the number of transformer layers to fine-tune. A Bayesian optimization strategy was employed, balancing exploration of the hyperparameter space and exploitation of promising configurations. The performance of each hyperparameter configuration was evaluated on the validation set, and the best configuration was selected based on the performance metric of interest.

\subsection{Model Training and Optimization}

The model training process relied on Binary Cross-Entropy (BCE) as the loss function for Track A and C, and Cross-Entropy for Track B due to its suitability for classification tasks. Optimization was performed using the \texttt{AdamW} optimizer, which improves upon the standard Adam optimizer by decoupling weight decay and learning rate updates \citep{Loshchilov2019AdamW}. To further enhance training stability and convergence, a cosine annealing learning rate scheduler with restarts was employed. This scheduling approach helped adaptively reduce the learning rate over time, facilitating better exploration of the loss landscape and improving generalization. The model was trained for a fixed number of epochs, and early stopping was used to terminate training if the validation performance plateaued, thus avoiding overfitting.

\subsection{Tools and Libraries}

The implementation of the experiments utilized several state-of-the-art tools and libraries. The deep learning models were implemented and trained using \texttt{PyTorch}, which provides a flexible and high-performance framework for machine learning research \citep{Paszke2019PyTorch}. For data manipulation and evaluation metrics, \texttt{Scikit-Learn} was employed \citep{Pedregosa2011ScikitLearn}. Gradient boosting models were benchmarked using \texttt{XGBoost}, which is widely regarded for its efficiency and scalability \citep{Chen2016XGBoost}. Pre-trained transformer models were fine-tuned using \texttt{Hugging Face Transformers}, a library that offers robust implementations of transformer-based architectures \citep{Wolf2019HuggingFace}. These tools and libraries are well-regarded in the machine learning community and were chosen for their reliability and performance.

\subsection{Postprocessing}

Postprocessing involved thresholding the model's output probabilities to convert them into binary class predictions. A default threshold of 0.5 was used, but sensitivity analyses were conducted to evaluate the impact of varying the threshold. This ensured that the model's performance was robust across different operating points and provided interpretable results for downstream tasks. Minimal additional postprocessing was applied to maintain the integrity of the model's predictions.

% \subsection{Concluding Remarks on Setup}

% The experimental setup was designed to maximize the reliability, reproducibility, and validity of the results. By adhering to established best practices in data splitting, preprocessing, and hyperparameter tuning, and by leveraging state-of-the-art tools and optimization strategies, the experimental methodology ensures a robust evaluation of the model's performance. Furthermore, the combination of advanced optimization techniques, careful preprocessing, and systematic model selection contributes to the study's alignment with the broader goals of advancing research in machine learning. This setup not only facilitates a fair comparison with existing methods but also provides a strong foundation for further exploration and improvement of the proposed approach.

### 2025-02-21 paper/sections/ExperimentalSetup.tex
add related work section

@@
 For data manipulation and evaluation metrics, \texttt{Scikit-Learn} was employed \citep{Pedregosa2011ScikitLearn}.
-Gradient boosting models were benchmarked using \texttt{XGBoost}, which is widely regarded for its efficiency and scalability \citep{Chen2016XGBoost}.
+Gradient boosting models were benchmarked using \texttt{XGBoost}, which is widely regarded for its efficiency and scalability \citep{chen2016xgboost}.
 Pre-trained transformer models were fine-tuned using \texttt{Hugging Face Transformers}, a library that offers robust implementations of transformer-based architectures \citep{Wolf2019HuggingFace}.

### 2025-02-21 paper/sections/RelatedWork.tex
add related work section

\section{Related Work}
Multi-label emotion detection has emerged as a significant task in natural language processing (NLP), particularly for low-resource languages. The task is structured in two main output formats: (1) a binary format, which indicates whether an emotion is present in the text, and (2) an intensity scale ranging from 0 to 3, which represents the strength of the emotion in the text.

Given that this task follows a text classification paradigm, various models have been explored to identify the most effective architectures. A considerable amount of research has focused on evaluating different structures to determine the optimal approach. In \cite{wang2016dimensional}, a combination of Long Short-Term Memory (LSTM) networks and Convolutional Neural Networks (CNNs) was explored, where various model configurations were compared based on their F1-score performances. These insights were leveraged to identify suitable model structures for developing a custom model tailored to the specific requirements of this task.

% \section{Related Works}
Several studies have addressed multi-label emotion detection, focusing on various model architectures and preprocessing strategies. In \cite{wang2016dimensional}, a comparative analysis of LSTM and CNN models was performed, demonstrating that hybrid architectures could enhance the F1-score performance of sentiment classification tasks. This research serves as a foundation for designing a model suited to the task at hand.

For low-resource languages, text preprocessing plays a crucial role in improving model performance. The work presented in \cite{muhammad2023semeval} highlighted the effectiveness of multiple preprocessing algorithms specifically designed for African languages. The study demonstrated that well-structured preprocessing pipelines lead to better text representations, ultimately improving classification accuracy.

Moreover, datasets specifically curated for emotion detection in underrepresented languages have been explored. The datasets presented in \cite{muhammad2025brighterbridginggaphumanannotated} and \cite{belay-etal-2025-evaluatin} serve as essential resources for training models and evaluating performance in real-world settings. These datasets enable the training of robust models capable of handling linguistic diversity.

To enhance model performance, modifications to existing architectures have been proposed. Based on the insights from \cite{wang2016dimensional}, additional layers were incorporated into custom models to improve the representation of low-resource languages. This ensures that the models can capture intricate linguistic patterns that might otherwise be overlooked.

### 2025-02-22 paper/sections/ExperimentalSetup.tex
add results

@@
 
-This section describes the experimental setup, providing details about data splits, preprocessing steps, hyperparameter tuning, and the tools and libraries utilized.
+This section describes the experimental setup, providing details about data splits, preprocessing steps, hyperparameter tuning, computational resources, and the tools and libraries utilized.
 The goal is to ensure reproducibility, transparency, and alignment with established best practices in machine learning research.
+\input{tables/MainResults}
 
 \subsection{Data Splits and Usage}
-
+%TODO: refer to dataset used
 The dataset was divided into three subsets: training, development (validation), and testing.
@@
 
+\subsection{Computational Resources}
+
+All experiments were run on a Kaggle Tesla P100 GPU, which provided the necessary computational power to efficiently train and evaluate the models.
+The use of a Tesla P100 allowed for accelerated processing, making it feasible to leverage complex models and extensive hyperparameter tuning within a reasonable timeframe.
+This setup ensures that the experiments are reproducible and can be replicated by other researchers with access to similar hardware.
+
 \subsection{Postprocessing}

### 2025-02-22 paper/sections/SystemOverview.tex
add results

@@
 The preprocessing pipeline involves multiple steps to clean and standardize the text data.
-Initially, all text is converted to lowercase and unnecessary whitespace is removed.
-Then, special characters, URLs, and emojis are filtered out using regular expressions.
-Each emoji is replaced by its corresponding title (e.g., \smiley → "smiling face").
+Initially, all text is converted to lowercase, and unnecessary whitespace is removed.
+Special characters, URLs, and emojis are filtered out using regular expressions.
+Emojis, in particular, are replaced with their corresponding textual descriptions (e.g., \smiley $\rightarrow$ ``smiling face'').
 Tokenization is performed using language-specific tokenizers to ensure optimal segmentation.
@@
 
+For languages with sufficient pretrained models available, we identified the best-performing embedding model and paired it with SVM as the classifier.
+This approach leverages the strengths of the pretrained embedding models in capturing language-specific nuances, while the SVM classifier ensures robust performance for multi-label classification.
+On the other hand, for languages with limited pretrained resources, we utilized the multilingual embedding model ``Multilingual-E5-large-instruct'' \citep{wang2024multilingual} in combination with XGBoost as the classifier.
+The ``Multilingual-E5-large-instruct'' model, designed to generalize across diverse languages, enabled the system to maintain high performance even in resource-constrained settings.
+
+\subsection{Summary of Model Variants}
+
 By combining these techniques, the proposed system captures rich linguistic representations of the input text and achieves accurate multi-label classification.

### 2025-02-22 paper/tables/MainResults.tex
add results

\begin{table*}[h]
    \centering
    \caption{Results across Track A, B, and C showing macro-average F1 scores of Our Model , Paraticipants Best Model scores, Task Dataset Model\citep{muhammad2025brighterbridginggaphumanannotated} and rankings.}
    \label{tab:results}
    \resizebox{2\columnwidth}{!}{
        \begin{tabular}{l|ccc|cccc|cccc}
            \hline
                              & \multicolumn{3}{c|}{Track A} & \multicolumn{4}{c|}{Track B} & \multicolumn{4}{c}{Track C}                                                                                                                                                     \\
            \cline{2-12}
            \textbf{Language} & \textbf{Our Model}               & \textbf{Best Model}          & \textbf{Rank}               & \textbf{Our Model} & \textbf{Best Model} & \textbf{Task Dataset Model} & \textbf{Rank} & \textbf{Our Model} & \textbf{Best Model} & \textbf{Task Dataset Model} & \textbf{Rank} \\
            \hline
            afr               & 54.01                        & 69.86                        & 15/37                       & —              & —                   & —                & —             & 54.01          & 70.50               & 61.28            & 4/14          \\
            amh               & 61.20                        & 77.31                        & 19/43                       & 49.42          & 85.58               & —                & 14/23         & 61.20          & 66.68               & —                & 6/13          \\
            arq               & 51.07                        & 66.87                        & 24/43                       & 36.54          & 63.38               & 36.37            & 18/26         & 51.07          & 65.35               & 55.75            & 6/14          \\
            ary               & 51.88                        & 62.92                        & 20/41                       & —              & —                   & —                & —             & 51.88          & 63.22               & 52.76            & 6/12          \\
            chn               & 56.65                        & 70.94                        & 30/41                       & 48.47          & 72.24               & 51.86            & 19/27         & 56.65          & 56.65               & 55.23            & 7/15          \\
            deu               & 60.60                        & 73.99                        & 25/50                       & 54.10          & 76.57               & 56.21            & 18/27         & 60.60          & 73.62               & 59.17            & 6/15          \\
            eng               & 73.97                        & 82.30                        & 35/96                       & 68.81          & 84.04               & 64.15            & 28/43         & 73.97          & 82.07               & 65.58            & 4/17          \\
            esp               & 76.19                        & 84.88                        & 26/47                       & 66.70          & 80.80               & 72.59            & 23/29         & 76.19          & 85.00               & 73.29            & 5/15          \\
            hau               & 63.22                        & 75.07                        & 18/40                       & 58.42          & 77.00               & 39.16            & 15/26         & 63.22          & 73.14               & 51.91            & 4/13          \\
            hin               & 80.32                        & 92.57                        & 33/43                       & —              & —                   & —                & —             & 80.32          & 92.16               & 79.73            & 6/16          \\
            ibo               & 50.93                        & 60.01                        & 14/34                       & —              & —                   & —                & —             & 50.93          & 60.47               & 37.40            & 4/12          \\
            ind               & —                            & —                            & —                           & —              & —                   & —                & —             & 35.64          & 67.24               & 57.29            & 15/17         \\
            jav               & —                            & —                            & —                           & —              & —                   & —                & —             & 25.62          & 25.62               & 50.47            & 12/13         \\
            kin               & 51.94                        & 65.74                        & 6/31                        & —              & —                   & —                & —             & 51.94          & 64.59               & 34.36            & 2/11          \\
            mar               & 81.10                        & 90.58                        & 23/42                       & —              & —                   & —                & —             & 81.10          & 90.42               & 77.24            & 6/13          \\
            orm               & 54.31                        & 61.64                        & 11/36                       & —              & —                   & —                & —             & 54.31          & 60.07               & —                & 3/11          \\
            pcm               & 53.09                        & 67.40                        & 22/34                       & —              & —                   & —                & —             & 53.09          & 67.40               & 48.67            & 5/10          \\
            ptbr              & 47.99                        & 68.33                        & 27/42                       & 38.20          & 71.00               & 46.72            & 22/25         & 47.99          & 68.36               & 51.60            & 8/14          \\
            ptmz              & 50.08                        & 54.77                        & 6/36                        & —              & —                   & —                & —             & 50.08          & 55.54               & 40.44            & 3/14          \\
            ron               & 73.75                        & 79.43                        & 14/43                       & 57.61          & 72.60               & 57.69            & 19/26         & 73.75          & 77.27               & 76.23            & 4/15          \\
            rus               & 82.42                        & 90.87                        & 33/50                       & 78.41          & 92.54               & 87.66            & 22/30         & 82.42          & 90.62               & 76.97            & 6/17          \\
            som               & 48.26                        & 57.65                        & 10/34                       & —              & —                   & —                & —             & 48.26          & 56.66               & —                & 4/13          \\
            sun               & 42.48                        & 54.97                        & 19/37                       & —              & —                   & —                & —             & 42.48          & 50.72               & 46.33            & 4/11          \\
            swa               & 29.52                        & 41.47                        & 15/32                       & —              & —                   & —                & —             & 29.52          & 38.43               & 33.27            & 5/14          \\
            swe               & 56.51                        & 62.62                        & 13/40                       & —              & —                   & —                & —             & 56.51          & 64.53               & 51.18            & 6/13          \\
            tat               & 64.32                        & 84.59                        & 18/36                       & —              & —                   & —                & —             & 64.32          & 83.59               & 60.66            & 5/11          \\
            tir               & 52.37                        & 59.05                        & 6/34                        & —              & —                   & —                & —             & 52.37          & 55.24               & —                & 2/10          \\
            ukr               & 48.62                        & 72.56                        & 29/40                       & 42.55          & 70.75               & 43.54            & 17/24         & 48.62          & 71.99               & 54.76            & 10/17         \\
            vmw               & 16.81                        & 32.50                        & 5/31                        & —              & —                   & —                & —             & 16.80          & 26.02               & 20.41            & 6/9           \\
            xho               & —                            & —                            & —                           & —              & —                   & —                & —             & 16.64          & 44.26               & 30.79            & 6/10          \\
            yor               & 34.09                        & 46.13                        & 9/32                        & —              & —                   & —                & —             & 34.09          & 46.79               & 27.44            & 4/11          \\
            zul               & —                            & —                            & —                           & —              & —                   & —                & —             & 16.35          & 16.35               & 22.03            & 8/11          \\
            \hline
        \end{tabular}
    }
\end{table*}

### 2025-02-22 paper/sections/Abstract.tex
add conclusion

\begin{abstract}
    salam.
    khobi.
\end{abstract}

### 2025-02-22 paper/sections/Conclusion.tex
add conclusion

\section{Conclusion}
This study investigated multilingual emotion classification, addressing the challenges of detecting and analyzing emotions across diverse linguistic contexts. By structuring the problem into three tracks: binary emotion classification, intensity estimation, and cross-lingual emotion detection—we evaluated multiple machine learning and deep learning approaches to improve emotion recognition across various languages. Our findings demonstrate the effectiveness of leveraging language-specific preprocessing techniques, domain adaptation strategies, and transfer learning in enhancing model performance.

The significance of this research lies in its contribution to multilingual emotion recognition, particularly for low-resource languages. Our methodology, integrating deep learning models such as LSTMs, transformer-based embeddings, and classification techniques like SVM and XGBoost, achieved competitive results in emotion classification tasks. The study underscores the importance of language-aware preprocessing and domain adaptation techniques in addressing linguistic diversity.

Despite the promising results, certain limitations persist. The scarcity of annotated data for many underrepresented languages remains a challenge, potentially impacting model generalization. Additionally, while the study explores multiple model architectures, further optimizations could enhance performance, particularly in cross-lingual settings. Future research should focus on expanding high-quality multilingual emotion datasets, exploring zero-shot learning approaches, and improving model interpretability to enhance emotion classification across diverse languages and cultural contexts.

By advancing multilingual emotion recognition, this research contributes to computational linguistics, social media analysis, and human-computer interaction, fostering better understanding of emotional expressions in multilingual communication.

### 2025-02-22 paper/sections/ExperimentalSetup.tex
add conclusion

@@
 \subsection{Data Splits and Usage}
-%TODO: refer to dataset used
-The dataset was divided into three subsets: training, development (validation), and testing.
+The dataset\cite{muhammad2025brighterbridginggaphumanannotated} was divided into three subsets: training, development (validation), and testing.
 Specifically, 80\% of the training dataset was allocated for training, while the remaining 20\% was reserved for validation to facilitate model selection.
@@
 The model training process relied on Binary Cross-Entropy (BCE) as the loss function for Track A and C, and Cross-Entropy for Track B due to its suitability for classification tasks.
+Given the unbalanced dataset, a weighted loss approach was employed to ensure that the model adequately learned from all classes.
 Optimization was performed using the \texttt{AdamW} optimizer, which improves upon the standard Adam optimizer by decoupling weight decay and learning rate updates \citep{Loshchilov2019AdamW}.

### 2025-02-22 paper/sections/RelatedWork.tex
add conclusion

@@
 Moreover, datasets specifically curated for emotion detection in underrepresented languages have been explored.
-The datasets presented in \cite{muhammad2025brighterbridginggaphumanannotated} and \cite{belay-etal-2025-evaluatin} serve as essential resources for training models and evaluating performance in real-world settings.
+The datasets presented in \cite{muhammad2025brighterbridginggaphumanannotated} and \cite{belay-etal-2025-evaluating} serve as essential resources for training models and evaluating performance in real-world settings.
 These datasets enable the training of robust models capable of handling linguistic diversity.

### 2025-02-22 paper/sections/SystemOverview.tex
add conclusion

@@
 Additionally, the system employed XGBoost, a gradient boosting framework renowned for its effectiveness in structured data classification \citep{chen2016xgboost}.
-Furthermore, Support Vector Machines (SVMs) were utilized as a classification method due to their ability to operate effectively in high-dimensional feature spaces by identifying optimal hyperplanes for classification \citep{cortes1995support}.
+Furthermore, SVMs\footnote{Support Vector Machines} were utilized as a classification method due to their ability to operate effectively in high-dimensional feature spaces by identifying optimal hyperplanes for classification \citep{cortes1995support}.
 
-For languages with sufficient pretrained models available, we identified the best-performing embedding model and paired it with SVM as the classifier.
+For languages with sufficient pretrained models available using MTEB\footnote{Massive Text Embedding Benchmark}\citep{muennighoff2022mteb}, we identified the best-performing embedding model and paired it with SVM as the classifier.
 This approach leverages the strengths of the pretrained embedding models in capturing language-specific nuances, while the SVM classifier ensures robust performance for multi-label classification.
-On the other hand, for languages with limited pretrained resources, we utilized the multilingual embedding model ``Multilingual-E5-large-instruct'' \citep{wang2024multilingual} in combination with XGBoost as the classifier.
-The ``Multilingual-E5-large-instruct'' model, designed to generalize across diverse languages, enabled the system to maintain high performance even in resource-constrained settings.
+On the other hand, for languages with limited pretrained resources, we utilized the multilingual embedding model "Multilingual E5 large instruct" \citep{wang2024multilingual} in combination with XGBoost as the classifier.
+The model, designed to generalize across diverse languages, enabled the system to maintain high performance even in resource-constrained settings.
 

### 2025-02-22 paper/tables/MainResults.tex
add conclusion

@@
+% Multilingual-E5-large-instruct \citep{wang2024multilingual}
+% AraBert Large Algerian \citep{arabert}
 \begin{table*}[h]
     \centering
-    \caption{Results across Track A, B, and C showing macro-average F1 scores of Our Model , Paraticipants Best Model scores, Task Dataset Model\citep{muhammad2025brighterbridginggaphumanannotated} and rankings.}
+    \caption{Results across Track A, B, and C showing macro-average F1 scores of Our Model , Paraticipants Best Model scores, Task Dataset Model(Baseline)\citep{muhammad2025brighterbridginggaphumanannotated} and rankings.}
     \label{tab:results}
     \resizebox{2\columnwidth}{!}{
-        \begin{tabular}{l|ccc|cccc|cccc}
+        \begin{tabular}{l|c|ccc|cccc|cccc}
             \hline
-                              & \multicolumn{3}{c|}{Track A} & \multicolumn{4}{c|}{Track B} & \multicolumn{4}{c}{Track C}                                                                                                                                                     \\
-            \cline{2-12}
-            \textbf{Language} & \textbf{Our Model}               & \textbf{Best Model}          & \textbf{Rank}               & \textbf{Our Model} & \textbf{Best Model} & \textbf{Task Dataset Model} & \textbf{Rank} & \textbf{Our Model} & \textbf{Best Model} & \textbf{Task Dataset Model} & \textbf{Rank} \\
+                                                    &                                                                                              & \multicolumn{3}{c|}{Track A} & \multicolumn{4}{c|}{Track B} & \multicolumn{4}{c}{Track C}                                                                                                                                         \\
+            \cline{3-13}
+            \textbf{Language}                       & \textbf{Our Model Name}                                                                      & \textbf{Ours}                & \textbf{Best}                & \textbf{Rank}               & \textbf{Ours} & \textbf{Best} & \textbf{Baseline} & \textbf{Rank} & \textbf{Ours} & \textbf{Best} & \textbf{Baseline} & \textbf{Rank} \\
             \hline
-            afr               & 54.01                        & 69.86                        & 15/37                       & —              & —                   & —                & —             & 54.01          & 70.50               & 61.28            & 4/14          \\
-            amh               & 61.20                        & 77.31                        & 19/43                       & 49.42          & 85.58               & —                & 14/23         & 61.20          & 66.68               & —                & 6/13          \\
-            arq               & 51.07                        & 66.87                        & 24/43                       & 36.54          & 63.38               & 36.37            & 18/26         & 51.07          & 65.35               & 55.75            & 6/14          \\
-            ary               & 51.88                        & 62.92                        & 20/41                       & —              & —                   & —                & —             & 51.88          & 63.22               & 52.76            & 6/12          \\
-            chn               & 56.65                        & 70.94                        & 30/41                       & 48.47          & 72.24               & 51.86            & 19/27         & 56.65          & 56.65               & 55.23            & 7/15          \\
-            deu               & 60.60                        & 73.99                        & 25/50                       & 54.10          & 76.57               & 56.21            & 18/27         & 60.60          & 73.62               & 59.17            & 6/15          \\
-            eng               & 73.97                        & 82.30                        & 35/96                       & 68.81          & 84.04               & 64.15            & 28/43         & 73.97          & 82.07               & 65.58            & 4/17          \\
-            esp               & 76.19                        & 84.88                        & 26/47                       & 66.70          & 80.80               & 72.59            & 23/29         & 76.19          & 85.00               & 73.29            & 5/15          \\
-            hau               & 63.22                        & 75.07                        & 18/40                       & 58.42          & 77.00               & 39.16            & 15/26         & 63.22          & 73.14               & 51.91            & 4/13          \\
-            hin               & 80.32                        & 92.57                        & 33/43                       & —              & —                   & —                & —             & 80.32          & 92.16               & 79.73            & 6/16          \\
-            ibo               & 50.93                        & 60.01                        & 14/34                       & —              & —                   & —                & —             & 50.93          & 60.47               & 37.40            & 4/12          \\
-            ind               & —                            & —                            & —                           & —              & —                   & —                & —             & 35.64          & 67.24               & 57.29            & 15/17         \\
-            jav               & —                            & —                            & —                           & —              & —                   & —                & —             & 25.62          & 25.62               & 50.47            & 12/13         \\
-            kin               & 51.94                        & 65.74                        & 6/31                        & —              & —                   & —                & —             & 51.94          & 64.59               & 34.36            & 2/11          \\
-            mar               & 81.10                        & 90.58                        & 23/42                       & —              & —                   & —                & —             & 81.10          & 90.42               & 77.24            & 6/13          \\
-            orm               & 54.31                        & 61.64                        & 11/36                       & —              & —                   & —                & —             & 54.31          & 60.07               & —                & 3/11          \\
-            pcm               & 53.09                        & 67.40                        & 22/34                       & —              & —                   & —                & —             & 53.09          & 67.40               & 48.67            & 5/10          \\
-            ptbr              & 47.99                        & 68.33                        & 27/42                       & 38.20          & 71.00               & 46.72            & 22/25         & 47.99          & 68.36               & 51.60            & 8/14          \\
-            ptmz              & 50.08                        & 54.77                        & 6/36                        & —              & —                   & —                & —             & 50.08          & 55.54               & 40.44            & 3/14          \\
-            ron               & 73.75                        & 79.43                        & 14/43                       & 57.61          & 72.60               & 57.69            & 19/26         & 73.75          & 77.27               & 76.23            & 4/15          \\
-            rus               & 82.42                        & 90.87                        & 33/50                       & 78.41          & 92.54               & 87.66            & 22/30         & 82.42          & 90.62               & 76.97            & 6/17          \\
-            som               & 48.26                        & 57.65                        & 10/34                       & —              & —                   & —                & —             & 48.26          & 56.66               & —                & 4/13          \\
-            sun               & 42.48                        & 54.97                        & 19/37                       & —              & —                   & —                & —             & 42.48          & 50.72               & 46.33            & 4/11          \\
-            swa               & 29.52                        & 41.47                        & 15/32                       & —              & —                   & —                & —             & 29.52          & 38.43               & 33.27            & 5/14          \\
-            swe               & 56.51                        & 62.62                        & 13/40                       & —              & —                   & —                & —             & 56.51          & 64.53               & 51.18            & 6/13          \\
-            tat               & 64.32                        & 84.59                        & 18/36                       & —              & —                   & —                & —             & 64.32          & 83.59               & 60.66            & 5/11          \\
-            tir               & 52.37                        & 59.05                        & 6/34                        & —              & —                   & —                & —             & 52.37          & 55.24               & —                & 2/10          \\
-            ukr               & 48.62                        & 72.56                        & 29/40                       & 42.55          & 70.75               & 43.54            & 17/24         & 48.62          & 71.99               & 54.76            & 10/17         \\
-            vmw               & 16.81                        & 32.50                        & 5/31                        & —              & —                   & —                & —             & 16.80          & 26.02               & 20.41            & 6/9           \\
-            xho               & —                            & —                            & —                           & —              & —                   & —                & —             & 16.64          & 44.26               & 30.79            & 6/10          \\
-            yor               & 34.09                        & 46.13                        & 9/32                        & —              & —                   & —                & —             & 34.09          & 46.79               & 27.44            & 4/11          \\
-            zul               & —                            & —                            & —                           & —              & —                   & —                & —             & 16.35          & 16.35               & 22.03            & 8/11          \\
+            Afrikaans(afr)                          & \citep{wang2024multilingual} + SVM                                                           & 54.01                        & 69.86                        & 15/37                       & —             & —             & —                 & —             & 54.01         & 70.50         & 61.28             & 4/14          \\
+            Amharic(amh)                            & \citep{arabert}               + SVM                                                          & 61.20                        & 77.31                        & 19/43                       & 49.42         & 85.58         & —                 & 14/23         & 61.20         & 66.68         & —                 & 6/13          \\
+            Algerian Arabic(arq)                    & \citep{wang2024multilingual}   + SVM                                                         & 51.07                        & 66.87                        & 24/43                       & 36.54         & 63.38         & 36.37             & 18/26         & 51.07         & 65.35         & 55.75             & 6/14          \\
+            Moroccan Arabic(ary)                    & \citep{wang2024multilingual}   + SVM                                                         & 51.88                        & 62.92                        & 20/41                       & —             & —             & —                 & —             & 51.88         & 63.22         & 52.76             & 6/12          \\
+            Chinese(chn)                            & ZPoint Large\footnote{\url{https://huggingface.co/iampanda/zpoint_large_embedding_zh}} + SVM & 56.65                        & 70.94                        & 30/41                       & 48.47         & 72.24         & 51.86             & 19/27         & 56.65         & 56.65         & 55.23             & 7/15          \\
+            German(deu)                             & \citep{wang2024multilingual}       + SVM                                                     & 60.60                        & 73.99                        & 25/50                       & 54.10         & 76.57         & 56.21             & 18/27         & 60.60         & 73.62         & 59.17             & 6/15          \\
+            English(eng)                            & \citep{zhang2025jasperstelladistillationsota}                                                & 73.97                        & 82.30                        & 35/96                       & 68.81         & 84.04         & 64.15             & 28/43         & 73.97         & 82.07         & 65.58             & 4/17          \\
+            Spanish(esp)                            & \citep{wang2024multilingual}      + SVM                                                      & 76.19                        & 84.88                        & 26/47                       & 66.70         & 80.80         & 72.59             & 23/29         & 76.19         & 85.00         & 73.29             & 5/15          \\
+            Hausa(hau)                              & \citep{dobler-demelo-2023-focus} + SVM                                                       & 63.22                        & 75.07                        & 18/40                       & 58.42         & 77.00         & 39.16             & 15/26         & 63.22         & 73.14         & 51.91             & 4/13          \\
+            Hindi(hin)                              & \citep{wang2024multilingual}  + SVM                                                          & 80.32                        & 92.57                        & 33/43                       & —             & —             & —                 & —             & 80.32         & 92.16         & 79.73             & 6/16          \\
+            Igbo(ibo)                               & \citep{wang2024multilingual}   + SVM                                                         & 50.93                        & 60.01                        & 14/34                       & —             & —             & —                 & —             & 50.93         & 60.47         & 37.40             & 4/12          \\
+            Indonesian(ind)                         & \citep{wang2024multilingual}   + XGB                                                         & —                            & —                            & —                           & —             & —             & —                 & —             & 35.64         & 67.24         & 57.29             & 15/17         \\
+            Javanese(jav)                           & \citep{wang2024multilingual}   + XGB                                                         & —                            & —                            & —                           & —             & —             & —                 & —             & 25.62         & 25.62         & 50.47             & 12/13         \\
+            Kinyarwanda(kin)                        & \citep{wang2024multilingual}  + SVM                                                          & 51.94                        & 65.74                        & 6/31                        & —             & —             & —                 & —             & 51.94         & 64.59         & 34.36             & 2/11          \\
+            Marathi(mar)                            & \citep{wang2024multilingual}   + SVM                                                         & 81.10                        & 90.58                        & 23/42                       & —             & —             & —                 & —             & 81.10         & 90.42         & 77.24             & 6/13          \\
+            Oromo(orm)                              & \citep{wang2024multilingual}    + SVM                                                        & 54.31                        & 61.64                        & 11/36                       & —             & —             & —                 & —             & 54.31         & 60.07         & —                 & 3/11          \\
+            Nigerian-Pidgin(pcm)                    & \citep{wang2024multilingual}   + SVM                                                         & 53.09                        & 67.40                        & 22/34                       & —             & —             & —                 & —             & 53.09         & 67.40         & 48.67             & 5/10          \\
+            Pt\footnote{Portuguese} Brazilian(ptbr) & \citep{souza2020bertimbau} + SVM                                                             & 47.99                        & 68.33                        & 27/42                       & 38.20         & 71.00         & 46.72             & 22/25         & 47.99         & 68.36         & 51.60             & 8/14          \\
+            Pt Mozambican(ptmz)                     & \citep{wang2024multilingual}   + SVM                                                         & 50.08                        & 54.77                        & 6/36                        & —             & —             & —                 & —             & 50.08         & 55.54         & 40.44             & 3/14          \\
+            Romanian(ron)                           & \citep{wang2024multilingual}     + SVM                                                       & 73.75                        & 79.43                        & 14/43                       & 57.61         & 72.60         & 57.69             & 19/26         & 73.75         & 77.27         & 76.23             & 4/15          \\
+            Russian(rus)                            & \citep{snegirev2025russianfocusedembeddersexplorationrumteb}     + SVM                       & 82.42                        & 90.87                        & 33/50                       & 78.41         & 92.54         & 87.66             & 22/30         & 82.42         & 90.62         & 76.97             & 6/17          \\
+            Somali(som)                             & \citep{wang2024multilingual}       + SVM                                                     & 48.26                        & 57.65                        & 10/34                       & —             & —             & —                 & —             & 48.26         & 56.66         & —                 & 4/13          \\
+            Sundanese(sun)                          & \citep{wang2024multilingual}      + SVM                                                      & 42.48                        & 54.97                        & 19/37                       & —             & —             & —                 & —             & 42.48         & 50.72         & 46.33             & 4/11          \\
+            Swahili(swa)                            & \citep{wang2024multilingual}      + SVM                                                      & 29.52                        & 41.47                        & 15/32                       & —             & —             & —                 & —             & 29.52         & 38.43         & 33.27             & 5/14          \\
+            Swedish(swe)                            & \citep{wang2024multilingual}     + SVM                                                       & 56.51                        & 62.62                        & 13/40                       & —             & —             & —                 & —             & 56.51         & 64.53         & 51.18             & 6/13          \\
+            Tatar(tat)                              & \citep{wang2024multilingual}    + SVM                                                        & 64.32                        & 84.59                        & 18/36                       & —             & —             & —                 & —             & 64.32         & 83.59         & 60.66             & 5/11          \\
+            Tigrinya(tir)                           & \citep{wang2024multilingual}    + SVM                                                        & 52.37                        & 59.05                        & 6/34                        & —             & —             & —                 & —             & 52.37         & 55.24         & —                 & 2/10          \\
+            Ukrainian(ukr)                          & \citep{sturua2024jinaembeddingsv3multilingualembeddingstask}   + SVM                         & 48.62                        & 72.56                        & 29/40                       & 42.55         & 70.75         & 43.54             & 17/24         & 48.62         & 71.99         & 54.76             & 10/17         \\
+            Emakhuwa(vmw)                           & \citep{sturua2024jinaembeddingsv3multilingualembeddingstask}   + SVM                         & 16.81                        & 32.50                        & 5/31                        & —             & —             & —                 & —             & 16.80         & 26.02         & 20.41             & 6/9           \\
+            isiXhosa(xho)                           & \citep{wang2024multilingual}     + XGB                                                       & —                            & —                            & —                           & —             & —             & —                 & —             & 16.64         & 44.26         & 30.79             & 6/10          \\
+            Yoruba(yor)                             & \citep{wang2024multilingual}     + SVM                                                       & 34.09                        & 46.13                        & 9/32                        & —             & —             & —                 & —             & 34.09         & 46.79         & 27.44             & 4/11          \\
+            isiZulu(zul)                            & \citep{wang2024multilingual}     + XGB                                                       & —                            & —                            & —                           & —             & —             & —                 & —             & 16.35         & 16.35         & 22.03             & 8/11          \\
             \hline

### 2025-02-23 paper/sections/Abstract.tex
add abstract

@@
 \begin{abstract}
-    salam.
-    khobi.
+This paper presents a comprehensive study on multilingual emotion classification, aimed at advancing the detection and analysis of emotions in textual data across diverse languages.
+The research is structured into three distinct tracks: binary emotion classification, intensity estimation, and cross-lingual emotion detection.
+To address challenges associated with linguistic variability and limited annotated data, we employ a combination of deep learning techniques, including Long Short-Term Memory networks, transformer-based embeddings fine-tuned via low-rank adaptation, and classifiers such as SVMs\footnote{Support Vector Machines} and XGBoost.
+Extensive experiments conducted on datasets covering both high and low resource languages demonstrate that innovative preprocessing and domain adaptation strategies significantly enhance model performance, as evidenced by competitive macro-average F1 scores.
+Despite these promising results, the study acknowledges limitations arising from the scarcity of annotated data in underrepresented languages and the inherent complexity of capturing nuanced emotional expressions.
+The findings underscore the importance of developing robust, language-aware emotion recognition systems and suggest that future research should focus on expanding multilingual datasets, refining model architectures, and exploring zero-shot learning techniques.
 \end{abstract}

### 2025-02-23 paper/sections/Conclusion.tex
add abstract

@@
 By structuring the problem into three tracks: binary emotion classification, intensity estimation, and cross-lingual emotion detection—we evaluated multiple machine learning and deep learning approaches to improve emotion recognition across various languages.
-Our findings demonstrate the effectiveness of leveraging language-specific preprocessing techniques, domain adaptation strategies, and transfer learning in enhancing model performance.
+Our findings demonstrate the effectiveness of leveraging innovative preprocessing techniques, domain adaptation strategies, and transfer learning in enhancing model performance.
 
@@
 Our methodology, integrating deep learning models such as LSTMs, transformer-based embeddings, and classification techniques like SVM and XGBoost, achieved competitive results in emotion classification tasks.
-The study underscores the importance of language-aware preprocessing and domain adaptation techniques in addressing linguistic diversity.
+The study underscores the importance of innovative preprocessing and domain adaptation techniques in addressing linguistic diversity.
 

### 2025-02-23 paper/sections/ExperimentalSetup.tex
add abstract

@@
 The goal is to ensure reproducibility, transparency, and alignment with established best practices in machine learning research.
-\input{tables/MainResults}
+% \input{tables/MainResults}
+\begin{table*}[h]
+    \centering
+    \caption{Results across Track A, B, and C showing macro-average F1 scores of Our Model , Paraticipants Best Model scores, Task Dataset Model(Baseline)\citep{muhammad2025brighterbridginggaphumanannotated} and rankings.}
+    \label{tab:results}
+    \resizebox{2\columnwidth}{!}{
+        \begin{tabular}{l|c|ccc|cccc|cccc}
+            \hline
+                                                    &                                                                                              & \multicolumn{3}{c|}{Track A} & \multicolumn{4}{c|}{Track B} & \multicolumn{4}{c}{Track C}                                                                                                                                         \\
+            \cline{3-13}
+            \textbf{Language}                       & \textbf{Our Model}                                                                           & \textbf{Ours}                & \textbf{Best}                & \textbf{Rank}               & \textbf{Ours} & \textbf{Best} & \textbf{Baseline} & \textbf{Rank} & \textbf{Ours} & \textbf{Best} & \textbf{Baseline} & \textbf{Rank} \\
+            \hline
+            Afrikaans(afr)                          & \citep{wang2024multilingual} + SVM                                                           & 54.01                        & 69.86                        & 15/37                       & —             & —             & —                 & —             & 54.01         & 70.50         & 61.28             & 4/14          \\
+            Amharic(amh)                            & \citep{arabert}               + SVM                                                          & 61.20                        & 77.31                        & 19/43                       & 49.42         & 85.58         & —                 & 14/23         & 61.20         & 66.68         & —                 & 6/13          \\
+            Algerian Arabic(arq)                    & \citep{wang2024multilingual}   + SVM                                                         & 51.07                        & 66.87                        & 24/43                       & 36.54         & 63.38         & 36.37             & 18/26         & 51.07         & 65.35         & 55.75             & 6/14          \\
+            Moroccan Arabic(ary)                    & \citep{wang2024multilingual}   + SVM                                                         & 51.88                        & 62.92                        & 20/41                       & —             & —             & —                 & —             & 51.88         & 63.22         & 52.76             & 6/12          \\
+            Chinese(chn)                            & ZPoint Large\footnote{\url{https://huggingface.co/iampanda/zpoint_large_embedding_zh}} + SVM & 56.65                        & 70.94                        & 30/41                       & 48.47         & 72.24         & 51.86             & 19/27         & 56.65         & 56.65         & 55.23             & 7/15          \\
+            German(deu)                             & \citep{wang2024multilingual}       + SVM                                                     & 60.60                        & 73.99                        & 25/50                       & 54.10         & 76.57         & 56.21             & 18/27         & 60.60         & 73.62         & 59.17             & 6/15          \\
+            English(eng)                            & \citep{zhang2025jasperstelladistillationsota}                                                & 73.97                        & 82.30                        & 35/96                       & 68.81         & 84.04         & 64.15             & 28/43         & 73.97         & 82.07         & 65.58             & 4/17          \\
+            Spanish(esp)                            & \citep{wang2024multilingual}      + SVM                                                      & 76.19                        & 84.88                        & 26/47                       & 66.70         & 80.80         & 72.59             & 23/29         & 76.19         & 85.00         & 73.29             & 5/15          \\
+            Hausa(hau)                              & \citep{dobler-demelo-2023-focus} + SVM                                                       & 63.22                        & 75.07                        & 18/40                       & 58.42         & 77.00         & 39.16             & 15/26         & 63.22         & 73.14         & 51.91             & 4/13          \\
+            Hindi(hin)                              & \citep{wang2024multilingual}  + SVM                                                          & 80.32                        & 92.57                        & 33/43                       & —             & —             & —                 & —             & 80.32         & 92.16         & 79.73             & 6/16          \\
+            Igbo(ibo)                               & \citep{wang2024multilingual}   + SVM                                                         & 50.93                        & 60.01                        & 14/34                       & —             & —             & —                 & —             & 50.93         & 60.47         & 37.40             & 4/12          \\
+            Indonesian(ind)                         & \citep{wang2024multilingual}   + XGB                                                         & —                            & —                            & —                           & —             & —             & —                 & —             & 35.64         & 67.24         & 57.29             & 15/17         \\
+            Javanese(jav)                           & \citep{wang2024multilingual}   + XGB                                                         & —                            & —                            & —                           & —             & —             & —                 & —             & 25.62         & 25.62         & 50.47             & 12/13         \\
+            Kinyarwanda(kin)                        & \citep{wang2024multilingual}  + SVM                                                          & 51.94                        & 65.74                        & 6/31                        & —             & —             & —                 & —             & 51.94         & 64.59         & 34.36             & 2/11          \\
+            Marathi(mar)                            & \citep{wang2024multilingual}   + SVM                                                         & 81.10                        & 90.58                        & 23/42                       & —             & —             & —                 & —             & 81.10         & 90.42         & 77.24             & 6/13          \\
+            Oromo(orm)                              & \citep{wang2024multilingual}    + SVM                                                        & 54.31                        & 61.64                        & 11/36                       & —             & —             & —                 & —             & 54.31         & 60.07         & —                 & 3/11          \\
+            Nigerian-Pidgin(pcm)                    & \citep{wang2024multilingual}   + SVM                                                         & 53.09                        & 67.40                        & 22/34                       & —             & —             & —                 & —             & 53.09         & 67.40         & 48.67             & 5/10          \\
+            Pt\footnote{Portuguese} Brazilian(ptbr) & \citep{souza2020bertimbau} + SVM                                                             & 47.99                        & 68.33                        & 27/42                       & 38.20         & 71.00         & 46.72             & 22/25         & 47.99         & 68.36         & 51.60             & 8/14          \\
+            Pt Mozambican(ptmz)                     & \citep{wang2024multilingual}   + SVM                                                         & 50.08                        & 54.77                        & 6/36                        & —             & —             & —                 & —             & 50.08         & 55.54         & 40.44             & 3/14          \\
+            Romanian(ron)                           & \citep{wang2024multilingual}     + SVM                                                       & 73.75                        & 79.43                        & 14/43                       & 57.61         & 72.60         & 57.69             & 19/26         & 73.75         & 77.27         & 76.23             & 4/15          \\
+            Russian(rus)                            & \citep{snegirev2025russianfocusedembeddersexplorationrumteb}     + SVM                       & 82.42                        & 90.87                        & 33/50                       & 78.41         & 92.54         & 87.66             & 22/30         & 82.42         & 90.62         & 76.97             & 6/17          \\
+            Somali(som)                             & \citep{wang2024multilingual}       + SVM                                                     & 48.26                        & 57.65                        & 10/34                       & —             & —             & —                 & —             & 48.26         & 56.66         & —                 & 4/13          \\
+            Sundanese(sun)                          & \citep{wang2024multilingual}      + SVM                                                      & 42.48                        & 54.97                        & 19/37                       & —             & —             & —                 & —             & 42.48         & 50.72         & 46.33             & 4/11          \\
+            Swahili(swa)                            & \citep{wang2024multilingual}      + SVM                                                      & 29.52                        & 41.47                        & 15/32                       & —             & —             & —                 & —             & 29.52         & 38.43         & 33.27             & 5/14          \\
+            Swedish(swe)                            & \citep{wang2024multilingual}     + SVM                                                       & 56.51                        & 62.62                        & 13/40                       & —             & —             & —                 & —             & 56.51         & 64.53         & 51.18             & 6/13          \\
+            Tatar(tat)                              & \citep{wang2024multilingual}    + SVM                                                        & 64.32                        & 84.59                        & 18/36                       & —             & —             & —                 & —             & 64.32         & 83.59         & 60.66             & 5/11          \\
+            Tigrinya(tir)                           & \citep{wang2024multilingual}    + SVM                                                        & 52.37                        & 59.05                        & 6/34                        & —             & —             & —                 & —             & 52.37         & 55.24         & —                 & 2/10          \\
+            Ukrainian(ukr)                          & \citep{sturua2024jinaembeddingsv3multilingualembeddingstask}   + SVM                         & 48.62                        & 72.56                        & 29/40                       & 42.55         & 70.75         & 43.54             & 17/24         & 48.62         & 71.99         & 54.76             & 10/17         \\
+            Emakhuwa(vmw)                           & \citep{sturua2024jinaembeddingsv3multilingualembeddingstask}   + SVM                         & 16.81                        & 32.50                        & 5/31                        & —             & —             & —                 & —             & 16.80         & 26.02         & 20.41             & 6/9           \\
+            isiXhosa(xho)                           & \citep{wang2024multilingual}     + XGB                                                       & —                            & —                            & —                           & —             & —             & —                 & —             & 16.64         & 44.26         & 30.79             & 6/10          \\
+            Yoruba(yor)                             & \citep{wang2024multilingual}     + SVM                                                       & 34.09                        & 46.13                        & 9/32                        & —             & —             & —                 & —             & 34.09         & 46.79         & 27.44             & 4/11          \\
+            isiZulu(zul)                            & \citep{wang2024multilingual}     + XGB                                                       & —                            & —                            & —                           & —             & —             & —                 & —             & 16.35         & 16.35         & 22.03             & 8/11          \\
+            \hline
+        \end{tabular}
+    }
+\end{table*}
 

### 2025-02-23 paper/sections/SystemOverview.tex
add abstract

@@
 Additionally, the system employed XGBoost, a gradient boosting framework renowned for its effectiveness in structured data classification \citep{chen2016xgboost}.
-Furthermore, SVMs\footnote{Support Vector Machines} were utilized as a classification method due to their ability to operate effectively in high-dimensional feature spaces by identifying optimal hyperplanes for classification \citep{cortes1995support}.
+Furthermore, SVMs were utilized as a classification method due to their ability to operate effectively in high-dimensional feature spaces by identifying optimal hyperplanes for classification \citep{cortes1995support}.
 

### 2025-02-23 paper/sections/introduction.tex
add abstract

@@
 To address these limitations, we present a comprehensive analysis of state-of-the-art methodologies and evaluate their effectiveness across multiple languages.
-Our findings highlight the critical role of language-specific preprocessing techniques, domain adaptation strategies, and transfer learning in improving multilingual emotion classification.
+Our findings highlight the critical role of innovative preprocessing techniques, domain adaptation strategies, and transfer learning in improving multilingual emotion classification.
 

### 2025-02-23 paper/tables/MainResults.tex
add abstract

--- 2025-02-22 paper/tables/MainResults.tex
@@
-\begin{table*}[h]
-    \centering
-    \caption{Results across Track A, B, and C showing macro-average F1 scores of Our Model , Paraticipants Best Model scores, Task Dataset Model\citep{muhammad2025brighterbridginggaphumanannotated} and rankings.}
-    \label{tab:results}
-    \resizebox{2\columnwidth}{!}{
-        \begin{tabular}{l|ccc|cccc|cccc}
-            \hline
-                              & \multicolumn{3}{c|}{Track A} & \multicolumn{4}{c|}{Track B} & \multicolumn{4}{c}{Track C}                                                                                                                                                     \\
-            \cline{2-12}
-            \textbf{Language} & \textbf{Our Model}               & \textbf{Best Model}          & \textbf{Rank}               & \textbf{Our Model} & \textbf{Best Model} & \textbf{Task Dataset Model} & \textbf{Rank} & \textbf{Our Model} & \textbf{Best Model} & \textbf{Task Dataset Model} & \textbf{Rank} \\
-            \hline
-            afr               & 54.01                        & 69.86                        & 15/37                       & —              & —                   & —                & —             & 54.01          & 70.50               & 61.28            & 4/14          \\
-            amh               & 61.20                        & 77.31                        & 19/43                       & 49.42          & 85.58               & —                & 14/23         & 61.20          & 66.68               & —                & 6/13          \\
-            arq               & 51.07                        & 66.87                        & 24/43                       & 36.54          & 63.38               & 36.37            & 18/26         & 51.07          & 65.35               & 55.75            & 6/14          \\
-            ary               & 51.88                        & 62.92                        & 20/41                       & —              & —                   & —                & —             & 51.88          & 63.22               & 52.76            & 6/12          \\
-            chn               & 56.65                        & 70.94                        & 30/41                       & 48.47          & 72.24               & 51.86            & 19/27         & 56.65          & 56.65               & 55.23            & 7/15          \\
-            deu               & 60.60                        & 73.99                        & 25/50                       & 54.10          & 76.57               & 56.21            & 18/27         & 60.60          & 73.62               & 59.17            & 6/15          \\
-            eng               & 73.97                        & 82.30                        & 35/96                       & 68.81          & 84.04               & 64.15            & 28/43         & 73.97          & 82.07               & 65.58            & 4/17          \\
-            esp               & 76.19                        & 84.88                        & 26/47                       & 66.70          & 80.80               & 72.59            & 23/29         & 76.19          & 85.00               & 73.29            & 5/15          \\
-            hau               & 63.22                        & 75.07                        & 18/40                       & 58.42          & 77.00               & 39.16            & 15/26         & 63.22          & 73.14               & 51.91            & 4/13          \\
-            hin               & 80.32                        & 92.57                        & 33/43                       & —              & —                   & —                & —             & 80.32          & 92.16               & 79.73            & 6/16          \\
-            ibo               & 50.93                        & 60.01                        & 14/34                       & —              & —                   & —                & —             & 50.93          & 60.47               & 37.40            & 4/12          \\
-            ind               & —                            & —                            & —                           & —              & —                   & —                & —             & 35.64          & 67.24               & 57.29            & 15/17         \\
-            jav               & —                            & —                            & —                           & —              & —                   & —                & —             & 25.62          & 25.62               & 50.47            & 12/13         \\
-            kin               & 51.94                        & 65.74                        & 6/31                        & —              & —                   & —                & —             & 51.94          & 64.59               & 34.36            & 2/11          \\
-            mar               & 81.10                        & 90.58                        & 23/42                       & —              & —                   & —                & —             & 81.10          & 90.42               & 77.24            & 6/13          \\
-            orm               & 54.31                        & 61.64                        & 11/36                       & —              & —                   & —                & —             & 54.31          & 60.07               & —                & 3/11          \\
-            pcm               & 53.09                        & 67.40                        & 22/34                       & —              & —                   & —                & —             & 53.09          & 67.40               & 48.67            & 5/10          \\
-            ptbr              & 47.99                        & 68.33                        & 27/42                       & 38.20          & 71.00               & 46.72            & 22/25         & 47.99          & 68.36               & 51.60            & 8/14          \\
-            ptmz              & 50.08                        & 54.77                        & 6/36                        & —              & —                   & —                & —             & 50.08          & 55.54               & 40.44            & 3/14          \\
-            ron               & 73.75                        & 79.43                        & 14/43                       & 57.61          & 72.60               & 57.69            & 19/26         & 73.75          & 77.27               & 76.23            & 4/15          \\
-            rus               & 82.42                        & 90.87                        & 33/50                       & 78.41          & 92.54               & 87.66            & 22/30         & 82.42          & 90.62               & 76.97            & 6/17          \\
-            som               & 48.26                        & 57.65                        & 10/34                       & —              & —                   & —                & —             & 48.26          & 56.66               & —                & 4/13          \\
-            sun               & 42.48                        & 54.97                        & 19/37                       & —              & —                   & —                & —             & 42.48          & 50.72               & 46.33            & 4/11          \\
-            swa               & 29.52                        & 41.47                        & 15/32                       & —              & —                   & —                & —             & 29.52          & 38.43               & 33.27            & 5/14          \\
-            swe               & 56.51                        & 62.62                        & 13/40                       & —              & —                   & —                & —             & 56.51          & 64.53               & 51.18            & 6/13          \\
-            tat               & 64.32                        & 84.59                        & 18/36                       & —              & —                   & —                & —             & 64.32          & 83.59               & 60.66            & 5/11          \\
-            tir               & 52.37                        & 59.05                        & 6/34                        & —              & —                   & —                & —             & 52.37          & 55.24               & —                & 2/10          \\
-            ukr               & 48.62                        & 72.56                        & 29/40                       & 42.55          & 70.75               & 43.54            & 17/24         & 48.62          & 71.99               & 54.76            & 10/17         \\
-            vmw               & 16.81                        & 32.50                        & 5/31                        & —              & —                   & —                & —             & 16.80          & 26.02               & 20.41            & 6/9           \\
-            xho               & —                            & —                            & —                           & —              & —                   & —                & —             & 16.64          & 44.26               & 30.79            & 6/10          \\
-            yor               & 34.09                        & 46.13                        & 9/32                        & —              & —                   & —                & —             & 34.09          & 46.79               & 27.44            & 4/11          \\
-            zul               & —                            & —                            & —                           & —              & —                   & —                & —             & 16.35          & 16.35               & 22.03            & 8/11          \\
-            \hline
-        \end{tabular}
-    }
-\end{table*}
+% Multilingual-E5-large-instruct \citep{wang2024multilingual}
+% AraBert Large Algerian \citep{arabert}

### 2025-02-24 paper/sections/Abstract.tex
initial version of paper without appendix

--- 2025-02-22 paper/sections/Abstract.tex
@@
 \begin{abstract}
-    salam.
-    khobi.
+    This paper explores multilingual emotion classification across binary classification, intensity estimation, and cross-lingual detection tasks.
+To address linguistic variability and limited annotated data, we evaluate various deep learning approaches, including transformer-based embeddings and traditional classifiers.
+After extensive experimentation, language-specific embedding models were selected as the final approach, given their superior ability to capture linguistic and cultural nuances.
+Experiments on high- and low-resource languages demonstrate that this method significantly improves performance, achieving competitive macro-average F1 scores.
+Despite these advances, challenges remain due to limited annotated data in underrepresented languages and the complexity of nuanced emotional expressions.
+The study highlights the need for robust, language-aware emotion recognition systems and emphasizes future directions, including expanding multilingual datasets, refining models.
 \end{abstract}

### 2025-02-24 paper/sections/Conclusion.tex
initial version of paper without appendix

@@
 \section{Conclusion}
-This study investigated multilingual emotion classification, addressing the challenges of detecting and analyzing emotions across diverse linguistic contexts.
+This study presented a comprehensive examination of multilingual multi-label emotion detection, addressing binary classification, intensity estimation, and cross-lingual detection tasks.
+Our findings indicate that language-specific embedding models, when paired with classifiers such as SVM and XGBoost, offer a robust approach to capturing the nuanced linguistic and cultural features inherent in diverse textual data.
+The experimental results, measured in competitive macro-average F1 scores, underscore the potential of these tailored models to bridge performance gaps, particularly in low-resource languages where data scarcity and complex grammatical structures present significant challenges.
+
+The significance of this research lies in its demonstration that integrating innovative preprocessing techniques with state-of-the-art embedding models can lead to substantial improvements in emotion recognition performance.
+This has broad implications for applications in social media analysis, behavioral research, and other domains where understanding nuanced emotional expressions is crucial.
+
+Nonetheless, certain limitations persist.
+The scarcity of annotated data in underrepresented languages and the inherent complexity of nuanced emotional expressions continue to impede model performance.
+Future research should focus on expanding multilingual datasets, refining preprocessing methods, and exploring novel architectures to enhance model generalization and adaptability.
+Additionally, fine-tuning multilingual models specifically for low-resource languages could significantly improve emotion detection accuracy in these contexts.
+Such efforts will be instrumental in advancing the field of multilingual emotion analysis and in developing more robust, language-aware emotion recognition systems.
+
+% This study investigated multilingual emotion classification, addressing the challenges of detecting and analyzing emotions across diverse linguistic contexts.
 By structuring the problem into three tracks: binary emotion classification, intensity estimation, and cross-lingual emotion detection—we evaluated multiple machine learning and deep learning approaches to improve emotion recognition across various languages.
@@
 
-The significance of this research lies in its contribution to multilingual emotion recognition, particularly for low-resource languages.
+% The significance of this research lies in its contribution to multilingual emotion recognition, particularly for low-resource languages.
 Our methodology, integrating deep learning models such as LSTMs, transformer-based embeddings, and classification techniques like SVM and XGBoost, achieved competitive results in emotion classification tasks.
@@
 
-Despite the promising results, certain limitations persist.
+% Despite the promising results, certain limitations persist.
 The scarcity of annotated data for many underrepresented languages remains a challenge, potentially impacting model generalization.
@@
 
-By advancing multilingual emotion recognition, this research contributes to computational linguistics, social media analysis, and human-computer interaction, fostering better understanding of emotional expressions in multilingual communication.
+% By advancing multilingual emotion recognition, this research contributes to computational linguistics, social media analysis, and human-computer interaction, fostering better understanding of emotional expressions in multilingual communication.

### 2025-02-24 paper/sections/ExperimentalSetup.tex
initial version of paper without appendix

--- 2025-02-22 paper/sections/ExperimentalSetup.tex
@@
 Preprocessing of the dataset was performed using the \texttt{clean-text} library.
-The preprocessing pipeline included standardizing the text by lowercasing all characters, removing special characters and punctuation, and normalizing tokens through contraction expansion and the elimination of redundant whitespace.
+The preprocessing pipeline involved multiple steps to clean and standardize the text data.
+Initially, all text was converted to lowercase, and unnecessary whitespace was removed to eliminate redundancy.
+Special characters, URLs, and emojis were filtered out using regular expressions, with emojis being replaced by their corresponding textual descriptions (e.g., \smiley $\rightarrow$ ``smiling face'').
+Punctuation was also removed, and  tokenization was performed using language-specific tokenizers to ensure optimal segmentation, and stopwords were removed to further reduce noise.
 These steps ensured the data was clean and consistent across all subsets.
-Details of the preprocessing pipeline are provided in the supplementary material (Appendix A).
 Preprocessing was applied consistently to the training, validation, and test datasets to avoid introducing biases or inconsistencies.
-Such preprocessing steps have been shown to improve the performance of natural language processing (NLP) models by reducing noise and simplifying the input representations \citep{Zhang2020DataPrep}.
+Such preprocessing steps have been shown to improve the performance of NLP models by reducing noise and simplifying the input representations \citep{Zhang2020DataPrep}.
 
@@
 Hyperparameter tuning was conducted using \texttt{Optuna}, an advanced framework for automated hyperparameter optimization \citep{Akiba2019Optuna}.
-The hyperparameters tuned included the learning rate, batch size, dropout rate, and the number of transformer layers to fine-tune.
+The hyperparameters tuned included the hyperparameters of SVM and XGBoost.
 A Bayesian optimization strategy was employed, balancing exploration of the hyperparameter space and exploitation of promising configurations.
@@
 Given the unbalanced dataset, a weighted loss approach was employed to ensure that the model adequately learned from all classes.
-Optimization was performed using the \texttt{AdamW} optimizer, which improves upon the standard Adam optimizer by decoupling weight decay and learning rate updates \citep{Loshchilov2019AdamW}.
-To further enhance training stability and convergence, a cosine annealing learning rate scheduler with restarts was employed.
+Optimization for fine-tuning deep learning models was performed using the \texttt{AdamW} optimizer, which improves upon the standard Adam optimizer by decoupling weight decay and learning rate updates \citep{Loshchilov2019AdamW}.
+To further enhance training stability and convergence, a cosine annealing learning rate scheduler with restarts\cite{loshchilov2017sgdrstochasticgradientdescent} was employed.
 This scheduling approach helped adaptively reduce the learning rate over time, facilitating better exploration of the loss landscape and improving generalization.
@@
 Pre-trained transformer models were fine-tuned using \texttt{Hugging Face Transformers}, a library that offers robust implementations of transformer-based architectures \citep{Wolf2019HuggingFace}.
+Additionally, the \texttt{Sentence Transformers}\cite{reimers-2019-sentence-bert}\cite{reimers-2020-multilingual-sentence-bert} library was used to load embedding models.
 These tools and libraries are well-regarded in the machine learning community and were chosen for their reliability and performance.
@@
 
-All experiments were run on a Kaggle Tesla P100 GPU, which provided the necessary computational power to efficiently train and evaluate the models.
-The use of a Tesla P100 allowed for accelerated processing, making it feasible to leverage complex models and extensive hyperparameter tuning within a reasonable timeframe.
-This setup ensures that the experiments are reproducible and can be replicated by other researchers with access to similar hardware.
+All experiments were conducted using a Kaggle Tesla P100 GPU, which delivered the computational power required to efficiently train and evaluate the models.
+The Tesla P100 enabled faster processing, allowing us to effectively utilize complex models and perform extensive hyperparameter tuning within a practical timeframe.
+This setup ensures that the experiments are reproducible and can be replicated by other researchers with access to comparable hardware.
 
-\subsection{Postprocessing}
+% \subsection{Postprocessing}
 
-Postprocessing involved thresholding the model's output probabilities to convert them into binary class predictions.
+% Postprocessing involved thresholding the model's output probabilities to convert them into binary class predictions.
 A default threshold of 0.5 was used, but sensitivity analyses were conducted to evaluate the impact of varying the threshold.

### 2025-02-24 paper/sections/RelatedWork.tex
initial version of paper without appendix

@@
 % \section{Related Works}
-Several studies have addressed multi-label emotion detection, focusing on various model architectures and preprocessing strategies.
+% Several studies have addressed multi-label emotion detection, focusing on various model architectures and preprocessing strategies.
 In \cite{wang2016dimensional}, a comparative analysis of LSTM and CNN models was performed, demonstrating that hybrid architectures could enhance the F1-score performance of sentiment classification tasks.

### 2025-02-24 paper/sections/SystemOverview.tex
initial version of paper without appendix

@@
 
-The preprocessing pipeline involves multiple steps to clean and standardize the text data.
-Initially, all text is converted to lowercase, and unnecessary whitespace is removed.
-Special characters, URLs, and emojis are filtered out using regular expressions.
-Emojis, in particular, are replaced with their corresponding textual descriptions (e.g., \smiley $\rightarrow$ ``smiling face'').
-Tokenization is performed using language-specific tokenizers to ensure optimal segmentation.
-Finally, stopwords are removed, and text normalization techniques, such as stemming or lemmatization, are applied where appropriate.
+The preprocessing pipeline involves several steps to clean and standardize the text data.
+These include converting text to lowercase, removing unnecessary whitespace, filtering out special characters, URLs, and emojis by replacing with their textual description, normalizing tokens, performing language-specific tokenization, and removing stopwords.
+These steps ensure the data is consistent and suitable for NLP\footnote{natural language processing} tasks.
 
@@
 
-To extract features, we employed a diverse range of models, including Long Short-Term Memory (LSTM) networks, multilingual language models, and Large Language Models (LLMs).
-The LLMs were fine-tuned using Low-Rank Adaptation (LoRA) \citep{hu2021lora}, a parameter-efficient tuning method that facilitates task-specific adaptation while maintaining computational efficiency.
+To extract features, we employed a diverse range of models, including LSTM\footnote{Long Short-Term Memory} networks, MLMs\footnote{Multilingual Language Models}, and LLMs\footnote{Large Language Models}.
+The LLMs were fine-tuned using LoRA\footnote{Low-Rank Adaptation} \citep{hu2021lora}, a parameter-efficient tuning method that facilitates task-specific adaptation while maintaining computational efficiency.
 
@@
 Following feature extraction, we applied multiple classification algorithms to perform the multi-label classification task.
-One of the classifiers used was the Multi-Layer Perceptron (MLP), a feedforward artificial neural network capable of modeling complex relationships between the extracted features and the target labels.
+One of the classifiers used was the MLP\footnote{Multi-Layer Perceptron}, a feedforward artificial neural network capable of modeling complex relationships between the extracted features and the target labels.
 Additionally, the system employed XGBoost, a gradient boosting framework renowned for its effectiveness in structured data classification \citep{chen2016xgboost}.
@@
 
-For languages with sufficient pretrained models available using MTEB\footnote{Massive Text Embedding Benchmark}\citep{muennighoff2022mteb}, we identified the best-performing embedding model and paired it with SVM as the classifier.
+For languages with sufficient pretrained models available using MTEB\footnote{Massive Text Embedding Benchmark}\citep{muennighoff2022mteb}, we identified the best-performing embedding model and paired it mainly with SVM as the classifier.
 This approach leverages the strengths of the pretrained embedding models in capturing language-specific nuances, while the SVM classifier ensures robust performance for multi-label classification.
-On the other hand, for languages with limited pretrained resources, we utilized the multilingual embedding model "Multilingual E5 large instruct" \citep{wang2024multilingual} in combination with XGBoost as the classifier.
+On the other hand, for languages with limited pretrained resources, we utilized the multilingual embedding model ``Multilingual E5 large instruct'' \citep{wang2024multilingual} in combination with XGBoost as the classifier.
 The model, designed to generalize across diverse languages, enabled the system to maintain high performance even in resource-constrained settings.

### 2025-02-24 paper/sections/introduction.tex
initial version of paper without appendix

@@
 This study focuses on the detection and classification of emotions across diverse linguistic contexts, spanning regions from South America to East Asia.
-Our objective is to categorize emotions into key dimensions, namely sadness, anger, fear, joy, and surprise, while considering cross-lingual variations and linguistic complexities.
+Our objective is to categorize emotions into key dimensions, namely sadness, anger, fear, disgust, joy, and surprise, while considering cross-lingual variations and linguistic complexities.
 

### 2025-02-24 paper/tables/MainResults.tex
initial version of paper without appendix

--- 2025-02-22 paper/tables/MainResults.tex
@@
-% Multilingual-E5-large-instruct \citep{wang2024multilingual}
-% AraBert Large Algerian \citep{arabert}
 \begin{table*}[h]
@@
             \cline{3-13}
-            \textbf{Language}                       & \textbf{Our Model Name}                                                                      & \textbf{Ours}                & \textbf{Best}                & \textbf{Rank}               & \textbf{Ours} & \textbf{Best} & \textbf{Baseline} & \textbf{Rank} & \textbf{Ours} & \textbf{Best} & \textbf{Baseline} & \textbf{Rank} \\
+            \textbf{Language}    & \textbf{Our Model}                                                     & \textbf{Ours}                & \textbf{Best}                & \textbf{Rank}               & \textbf{Ours} & \textbf{Best} & \textbf{Baseline} & \textbf{Rank} & \textbf{Ours} & \textbf{Best} & \textbf{Baseline} & \textbf{Rank} \\
             \hline
@@
             Moroccan Arabic(ary) & \citep{wang2024multilingual}   + SVM                                   & 51.88                        & 62.92                        & 20/41                       & —             & —             & —                 & —             & 51.88         & 63.22         & 52.76             & 6/12          \\
-            Chinese(chn)                            & ZPoint Large\footnote{\url{https://huggingface.co/iampanda/zpoint_large_embedding_zh}} + SVM & 56.65                        & 70.94                        & 30/41                       & 48.47         & 72.24         & 51.86             & 19/27         & 56.65         & 56.65         & 55.23             & 7/15          \\
+            Chinese(chn)         & \citep{zpoint-large-embedding-zh} + SVM                                & 56.65                        & 70.94                        & 30/41                       & 48.47         & 72.24         & 51.86             & 19/27         & 56.65         & 56.65         & 55.23             & 7/15          \\
             German(deu)          & \citep{wang2024multilingual}       + SVM                               & 60.60                        & 73.99                        & 25/50                       & 54.10         & 76.57         & 56.21             & 18/27         & 60.60         & 73.62         & 59.17             & 6/15          \\
-            English(eng)                            & \citep{zhang2025jasperstelladistillationsota}                                                & 73.97                        & 82.30                        & 35/96                       & 68.81         & 84.04         & 64.15             & 28/43         & 73.97         & 82.07         & 65.58             & 4/17          \\
+            English(eng)         & \citep{zhang2025jasperstelladistillationsota}  + SVM                   & 73.97                        & 82.30                        & 35/96                       & 68.81         & 84.04         & 64.15             & 28/43         & 73.97         & 82.07         & 65.58             & 4/17          \\
             Spanish(esp)         & \citep{wang2024multilingual}      + SVM                                & 76.19                        & 84.88                        & 26/47                       & 66.70         & 80.80         & 72.59             & 23/29         & 76.19         & 85.00         & 73.29             & 5/15          \\
@@
             Nigerian-Pidgin(pcm) & \citep{wang2024multilingual}   + SVM                                   & 53.09                        & 67.40                        & 22/34                       & —             & —             & —                 & —             & 53.09         & 67.40         & 48.67             & 5/10          \\
-            Pt\footnote{Portuguese} Brazilian(ptbr) & \citep{souza2020bertimbau} + SVM                                                             & 47.99                        & 68.33                        & 27/42                       & 38.20         & 71.00         & 46.72             & 22/25         & 47.99         & 68.36         & 51.60             & 8/14          \\
-            Pt Mozambican(ptmz)                     & \citep{wang2024multilingual}   + SVM                                                         & 50.08                        & 54.77                        & 6/36                        & —             & —             & —                 & —             & 50.08         & 55.54         & 40.44             & 3/14          \\
+            Pt* Brazilian(ptbr)  & \citep{souza2020bertimbau} + SVM                                       & 47.99                        & 68.33                        & 27/42                       & 38.20         & 71.00         & 46.72             & 22/25         & 47.99         & 68.36         & 51.60             & 8/14          \\
+            Pt* Mozambican(ptmz) & \citep{wang2024multilingual}   + SVM                                   & 50.08                        & 54.77                        & 6/36                        & —             & —             & —                 & —             & 50.08         & 55.54         & 40.44             & 3/14          \\
             Romanian(ron)        & \citep{wang2024multilingual}     + SVM                                 & 73.75                        & 79.43                        & 14/43                       & 57.61         & 72.60         & 57.69             & 19/26         & 73.75         & 77.27         & 76.23             & 4/15          \\
@@
             \hline
+            % \\
+            % \bottomrule
         \end{tabular}
     }
+    \\
+    \footnotesize{\textit{*: pt=Portuguese}}
 \end{table*}

### 2025-02-24 paper/appendix/ModelSelection.tex
add appendix

\section{Model Selection}
\label{sec:appendix_model_selection}
The training dataset of Track A was utilized for model selection, where it was split into an 80/20 ratio to create a training set and a validation set. Several models were evaluated on this split to identify the optimal model based on performance metrics such as recall, precision, and F1-score. The model that achieved the best balance across these metrics was selected as the final model and applied consistently across all three tracks—A, B, and C. A detailed comparative analysis of the performance of different models for each language is presented in Table \ref{tab:model_selection}, where each row corresponds to a specific language and includes results for multiple models, with columns reporting recall, precision, and F1-score for each.

\input{tables/ModelSelection}

Table \ref{tab:model_selection} provides a comprehensive comparison of the models' performance for each language, aiding in the selection of the final model applied to Tracks A, B, and C.

### 2025-02-26 paper/sections/ExperimentalSetup.tex
solved supervisor comments

@@
 Initially, all text was converted to lowercase, and unnecessary whitespace was removed to eliminate redundancy.
-Special characters, URLs, and emojis were filtered out using regular expressions, with emojis being replaced by their corresponding textual descriptions (e.g., \smiley $\rightarrow$ ``smiling face'').
+Special characters, URLs, and emojis were filtered out using regular expressions.
+Emojis were replaced by their corresponding textual descriptions (e.g., \smiley $\rightarrow$ ``smiling face'').
 Punctuation was also removed, and  tokenization was performed using language-specific tokenizers to ensure optimal segmentation, and stopwords were removed to further reduce noise.
@@
 
-The model training process relied on Binary Cross-Entropy (BCE) as the loss function for Track A and C, and Cross-Entropy for Track B due to its suitability for classification tasks.
+The model fine-tuning with LoRA, and the training of the MLP and XGBoost models, utilized Binary Cross-Entropy (BCE) as the loss function for Tracks A and C, and Cross-Entropy for Track B, owing to its appropriateness for classification tasks.
+Meanwhile, the training of the SVM model employed hinge loss.Using LoRA, we fine-tuned the Q, K, and V matrices for feature extractor transformer models, as shown in Table \ref{tab:model_selection}.
 Given the unbalanced dataset, a weighted loss approach was employed to ensure that the model adequately learned from all classes.

### 2025-02-26 paper/sections/RelatedWork.tex
solved supervisor comments

@@
 \section{Related Work}
-Multi-label emotion detection has emerged as a significant task in natural language processing (NLP), particularly for low-resource languages.
+Multi-label emotion detection has emerged as a significant task in NLP\footnote{natural language processing}, particularly for low-resource languages.
 The task is structured in two main output formats: (1) a binary format, which indicates whether an emotion is present in the text, and (2) an intensity scale ranging from 0 to 3, which represents the strength of the emotion in the text.
@@
 A considerable amount of research has focused on evaluating different structures to determine the optimal approach.
-In \cite{wang2016dimensional}, a combination of Long Short-Term Memory (LSTM) networks and Convolutional Neural Networks (CNNs) was explored, where various model configurations were compared based on their F1-score performances.
+In \cite{wang2016dimensional}, a combination of LSTM\footnote{Long Short-Term Memory} networks and CNNs\footnote{Convolutional Neural Networks} was explored, where various model configurations were compared based on their F1-score performances.
 These insights were leveraged to identify suitable model structures for developing a custom model tailored to the specific requirements of this task.

### 2025-02-26 paper/sections/SystemOverview.tex
solved supervisor comments

@@
 These include converting text to lowercase, removing unnecessary whitespace, filtering out special characters, URLs, and emojis by replacing with their textual description, normalizing tokens, performing language-specific tokenization, and removing stopwords.
-These steps ensure the data is consistent and suitable for NLP\footnote{natural language processing} tasks.
+These steps ensure the data is consistent and suitable for NLP tasks.
 
@@
 
-To extract features, we employed a diverse range of models, including LSTM\footnote{Long Short-Term Memory} networks, MLMs\footnote{Multilingual Language Models}, and LLMs\footnote{Large Language Models}.
+To extract features, we employed a diverse range of models, including LSTM networks, MLMs\footnote{Multilingual Language Models}, and LLMs\footnote{Large Language Models}.
 The LLMs were fine-tuned using LoRA\footnote{Low-Rank Adaptation} \citep{hu2021lora}, a parameter-efficient tuning method that facilitates task-specific adaptation while maintaining computational efficiency.
@@
 
-\subsection{Summary of Model Variants}
+% \subsection{Summary of Model Variants}
 
-By combining these techniques, the proposed system captures rich linguistic representations of the input text and achieves accurate multi-label classification.
+% By combining these techniques, the proposed system captures rich linguistic representations of the input text and achieves accurate multi-label classification.
 The experimental setup and evaluation metrics used to validate the effectiveness of this approach are discussed in subsequent sections.

### 2025-02-27 paper/sections/Abstract.tex
solved second supervisor comments

@@
 Experiments on high- and low-resource languages demonstrate that this method significantly improves performance, achieving competitive macro-average F1 scores.
+Notably, in languages such as Tigrinya and Kinyarwanda for cross-lingual detection task, our approach achieved a second-place ranking, driven by the incorporation of advanced preprocessing techniques.
 Despite these advances, challenges remain due to limited annotated data in underrepresented languages and the complexity of nuanced emotional expressions.
-The study highlights the need for robust, language-aware emotion recognition systems and emphasizes future directions, including expanding multilingual datasets, refining models.
+The study highlights the need for robust, language-aware emotion recognition systems and emphasizes future directions, including expanding multilingual datasets and refining models.
 \end{abstract}

### 2025-02-27 paper/sections/Conclusion.tex
solved second supervisor comments

@@
 
-Nonetheless, certain limitations persist.
-The scarcity of annotated data in underrepresented languages and the inherent complexity of nuanced emotional expressions continue to impede model performance.
-Future research should focus on expanding multilingual datasets, refining preprocessing methods, and exploring novel architectures to enhance model generalization and adaptability.
-Additionally, fine-tuning multilingual models specifically for low-resource languages could significantly improve emotion detection accuracy in these contexts.
-Such efforts will be instrumental in advancing the field of multilingual emotion analysis and in developing more robust, language-aware emotion recognition systems.
+Nonetheless, current limitations in multilingual emotion analysis include the lack of annotated data for underrepresented languages and challenges in capturing nuanced emotional expressions, both of which hinder model performance.
+Future research should prioritize expanding multilingual datasets, improving preprocessing techniques, and developing new architectures to boost model generalization and adaptability.
+Fine-tuning models for low-resource languages could also enhance emotion detection accuracy, advancing the field and creating more effective, language-aware emotion recognition systems.
 

### 2025-02-27 paper/sections/ExperimentalSetup.tex
solved second supervisor comments

@@
 The goal is to ensure reproducibility, transparency, and alignment with established best practices in machine learning research.
-\input{tables/MainResults}
+\begin{figure*}[t]
+    \centering
+    \includegraphics[width=1.7\columnwidth]{images/confusion_matrices_all_tracks.png}
+    \caption{Confusion matrices for each language across Tracks A, B, and C.}
+    \label{fig:confusion_matrices}
+\end{figure*}
 
@@
 
-Hyperparameter tuning was conducted using \texttt{Optuna}, an advanced framework for automated hyperparameter optimization \citep{Akiba2019Optuna}.
-The hyperparameters tuned included the hyperparameters of SVM and XGBoost.
-A Bayesian optimization strategy was employed, balancing exploration of the hyperparameter space and exploitation of promising configurations.
-The performance of each hyperparameter configuration was evaluated on the validation set, and the best configuration was selected based on the performance metric of interest.
+Hyperparameter tuning used Optuna \citep{Akiba2019Optuna} to optimize SVM and XGBoost hyperparameters.
+Bayesian optimization balanced exploration and exploitation, with configurations assessed on the validation set.
+The best configuration was selected based on the performance metric.
 
@@
 The model was trained for a fixed number of epochs, and early stopping was used to terminate training if the validation performance plateaued, thus avoiding overfitting.
+\input{tables/ErrorAnalysis}
 
@@
 The implementation of the experiments utilized several state-of-the-art tools and libraries.
-The deep learning models were implemented and trained using \texttt{PyTorch}, which provides a flexible and high-performance framework for machine learning research \citep{Paszke2019PyTorch}.
+The deep learning models were implemented and trained using \texttt{PyTorch} \citep{Paszke2019PyTorch}.
 For data manipulation and evaluation metrics, \texttt{Scikit-Learn} was employed \citep{Pedregosa2011ScikitLearn}.
-Gradient boosting models were benchmarked using \texttt{XGBoost}, which is widely regarded for its efficiency and scalability \citep{chen2016xgboost}.
-Pre-trained transformer models were fine-tuned using \texttt{Hugging Face Transformers}, a library that offers robust implementations of transformer-based architectures \citep{Wolf2019HuggingFace}.
-Additionally, the \texttt{Sentence Transformers}\cite{reimers-2019-sentence-bert}\cite{reimers-2020-multilingual-sentence-bert} library was used to load embedding models.
+Gradient boosting models were benchmarked using \texttt{XGBoost} \citep{chen2016xgboost}.
+Pre-trained transformer models were fine-tuned using \texttt{Hugging Face Transformers} \citep{Wolf2019HuggingFace}.
+Additionally, the \texttt{Sentence Transformers} library was used to load embedding models \cite{reimers-2019-sentence-bert}\cite{reimers-2020-multilingual-sentence-bert}.
 These tools and libraries are well-regarded in the machine learning community and were chosen for their reliability and performance.
@@
 
-All experiments were conducted using a Kaggle Tesla P100 GPU, which delivered the computational power required to efficiently train and evaluate the models.
-The Tesla P100 enabled faster processing, allowing us to effectively utilize complex models and perform extensive hyperparameter tuning within a practical timeframe.
-This setup ensures that the experiments are reproducible and can be replicated by other researchers with access to comparable hardware.
+Experiments used a Kaggle Tesla P100 GPU for efficient model training, evaluation, and hyperparameter tuning, ensuring reproducibility with comparable hardware.
 

### 2025-02-27 paper/tables/ErrorAnalysis.tex
solved second supervisor comments

\begin{table*}[h!]
    \centering
    \resizebox{2\columnwidth}{!}{
        \begin{tabular}{|p{12cm}|c|c|c|c|c|c|}
            \hline
            \textbf{Text}                                                                                                                                                                                                                                                                           & \textbf{Type} & \textbf{Anger} & \textbf{Fear} & \textbf{Joy} & \textbf{Sadness} & \textbf{Surprise} \\ \hline
            \multirow{2}{12cm}{I'm just numb.}                                                                                                                                                                                                                                                      & Truth         & 0              & 0             & 0            & 1                & 0                 \\ \cline{2-7}
                                                                                                                                                                                                                                                                                                    & Pred          & 0              & 1             & 0            & 1                & 0                 \\ \hline
            \multirow{2}{12cm}{At the time it didn't seem to bother me.}                                                                                                                                                                                                                            & Truth         & 0              & 0             & 0            & 1                & 0                 \\ \cline{2-7}
                                                                                                                                                                                                                                                                                                    & Pred          & 0              & 0             & 0            & 0                & 0                 \\ \hline
            \multirow{2}{12cm}{I found out six weeks before                                                                                                                     the wedding that my dad had only six weeks to live (he had cancer for two years... a fact she was fully aware of).} & Truth         & 1              & 1             & 0            & 1                & 1                 \\ \cline{2-7}
                                                                                                                                                                                                                                                                                                    & Pred          & 0              & 1             & 0            & 1                & 0                 \\ \hline
        \end{tabular}
    }
    \caption{Error Analysis Table of language English for track A}
    \label{tab:error_analysis}
\end{table*}

### 2025-02-27 paper/tables/MainResults.tex
complete Appendix
update rankings

--- 2025-02-23 paper/tables/MainResults.tex
@@
-% Multilingual-E5-large-instruct \citep{wang2024multilingual}
-% AraBert Large Algerian \citep{arabert}
+\begin{table*}[h]
+    \centering
+    \caption{Results across Track A, B, and C showing macro-average F1 scores of Our Model , Paraticipants Best Model scores, Task Dataset Best Model with Baseline\citep{muhammad2025brighterbridginggaphumanannotated} and rankings.}
+    \label{tab:results}
+    \resizebox{2\columnwidth}{!}{
+        \begin{tabular}{l|c|cccc|ccccc|ccccc}
+            \hline
+                                   &                                                                        & \multicolumn{4}{c|}{Track A} & \multicolumn{5}{c|}{Track B} & \multicolumn{5}{c}{Track C}                                                                                                                                                                               \\
+            \cline{3-16}
+            \textbf{Language}      & \textbf{Our Model}                                                     & \textbf{Ours}                & \textbf{BP*}                 & \textbf{Base}               & \textbf{Rank} & \textbf{Ours} & \textbf{BP*} & \textbf{BDP**} & \textbf{Base} & \textbf{Rank} & \textbf{Ours} & \textbf{BP*} & \textbf{BDP**} & \textbf{Base} & \textbf{Rank} \\
+            \hline
+            Afrikaans(afr)         & \citep{wang2024multilingual} + SVM                                     & 54.01                        & 69.86                        & 37.14                       & 15/39         & —             & —           & —              & —             & —             & 54.01         & 70.50       & 61.28          & 35.04         & 4/15          \\
+            Amharic(amh)           & \citep{arabert}               + SVM                                    & 61.20                        & 77.31                        & 63.83                       & 20/45         & 49.42         & 85.58       & —              & 50.79         & 15/24         & 61.20         & 66.68       & —              & 48.66         & 6/14          \\
+            Algerian Arabic(arq)   & \citep{wang2024multilingual}   + SVM                                   & 51.07                        & 66.87                        & 41.41                       & 24/45         & 36.54         & 64.97       & 36.37          & 1.64          & 18/27         & 51.07         & 65.35       & 55.75          & 33.78         & 6/15          \\
+            Moroccan Arabic(ary)   & \citep{wang2024multilingual}   + SVM                                   & 51.88                        & 62.92                        & 47.16                       & 20/43         & —             & —           & —              & —             & —             & 51.88         & 63.22       & 52.76          & 35.46         & 6/13          \\
+            Chinese(chn)           & \citep{zpoint-large-embedding-zh} + SVM                                & 56.65                        & 70.94                        & 53.08                       & 30/43         & 48.47         & 72.24       & 51.86          & 40.53         & 19/28         & 56.65         & 68.89       & 55.23          & 24.56         & 7/16          \\
+            German(deu)            & \citep{wang2024multilingual}       + SVM                               & 60.60                        & 73.99                        & 64.23                       & 26/52         & 54.10         & 76.57       & 56.21          & 56.21         & 19/28         & 60.60         & 73.62       & 59.17          & 46.84         & 6/16          \\
+            English(eng)           & \citep{zhang2025jasperstelladistillationsota}  + SVM                   & 73.97                        & 82.30                        & 70.83                       & 35/98         & 68.81         & 84.04       & 64.15          & 64.15         & 28/45         & 73.97         & 82.07       & 65.58          & 37.54         & 4/18          \\
+            Spanish(esp)           & \citep{wang2024multilingual}      + SVM                                & 76.19                        & 84.88                        & 77.44                       & 28/49         & 66.70         & 80.80       & 72.59          & 72.59         & 24/30         & 76.19         & 85.00       & 73.29          & 57.37         & 5/16          \\
+            Hausa(hau)             & \citep{dobler-demelo-2023-focus} + SVM                                 & 63.22                        & 75.07                        & 59.55                       & 18/42         & 58.42         & 77.00       & 39.16          & 27.03         & 15/27         & 63.22         & 73.14       & 51.91          & 31.98         & 4/14          \\
+            Hindi(hin)             & \citep{wang2024multilingual}  + SVM                                    & 80.32                        & 92.57                        & 85.51                       & 35/45         & —             & —           & —              & —             & —             & 80.32         & 92.16       & 79.73          & 13.75         & 6/17          \\
+            Igbo(ibo)              & \citep{wang2024multilingual}   + SVM                                   & 50.93                        & 60.01                        & 47.90                       & 14/36         & —             & —           & —              & —             & —             & 50.93         & 60.47       & 37.40          & 50.93         & 4/13          \\
+            Indonesian(ind)        & \citep{wang2024multilingual}   + XGB                                   & —                            & —                            & —                           & —             & —             & —           & —              & —             & —             & 35.64         & 67.24       & 57.29          & 37.64         & 16/18         \\
+            Javanese(jav)          & \citep{wang2024multilingual}   + XGB                                   & —                            & —                            & —                           & —             & —             & —           & —              & —             & —             & 25.62         & 46.38       & 50.47          & 46.38         & 13/14         \\
+            Kinyarwanda(kin)       & \citep{wang2024multilingual}  + SVM                                    & 51.94                        & 65.74                        & 46.29                       & 6/33          & —             & —           & —              & —             & —             & 51.94         & 64.59       & 34.36          & 18.38         & 2/12          \\
+            Marathi(mar)           & \citep{wang2024multilingual}   + SVM                                   & 81.10                        & 90.58                        & 82.20                       & 25/44         & —             & —           & —              & —             & —             & 81.10         & 90.42       & 77.24          & 77.24         & 6/14          \\
+            Oromo(orm)             & \citep{wang2024multilingual}    + SVM                                  & 54.31                        & 61.64                        & 12.63                       & 11/38         & —             & —           & —              & —             & —             & 54.31         & 60.07       & —              & 26.17         & 3/12          \\
+            Nigerian-Pidgin(pcm)   & \citep{wang2024multilingual}   + SVM                                   & 53.09                        & 67.40                        & 55.50                       & 23/36         & —             & —           & —              & —             & —             & 53.09         & 67.40       & 48.67          & 1.01          & 5/11          \\
+            Pt*** Brazilian(ptbr)  & \citep{souza2020bertimbau} + SVM                                       & 47.99                        & 68.33                        & 42.57                       & 28/44         & 38.20         & 71.00       & 46.72          & 29.74         & 22/26         & 47.99         & 68.36       & 51.60          & 41.84         & 8/15          \\
+            Pt*** Mozambican(ptmz) & \citep{wang2024multilingual}   + SVM                                   & 50.08                        & 54.77                        & 45.91                       & 6/38          & —             & —           & —              & —             & —             & 50.08         & 55.54       & 40.44          & 29.67         & 3/15          \\
+            Romanian(ron)          & \citep{wang2024multilingual}     + SVM                                 & 73.75                        & 79.43                        & 76.23                       & 15/45         & 57.61         & 72.60       & 57.69          & 55.66         & 18/27         & 73.75         & 77.27       & 76.23          & 76.23         & 5/16          \\
+            Russian(rus)           & \citep{snegirev2025russianfocusedembeddersexplorationrumteb}     + SVM & 82.42                        & 90.87                        & 83.77                       & 34/52         & 78.41         & 92.54       & 87.66          & 87.66         & 23/31         & 82.42         & 90.62       & 76.97          & 70.43         & 6/18          \\
+            Somali(som)            & \citep{wang2024multilingual}       + SVM                               & 48.26                        & 57.65                        & 45.93                       & 10/36         & —             & —           & —              & —             & —             & 48.26         & 56.66       & —              & 27.27         & 4/14          \\
+            Sundanese(sun)         & \citep{wang2024multilingual}      + SVM                                & 42.48                        & 54.97                        & 37.31                       & 20/39         & —             & —           & —              & —             & —             & 42.48         & 50.72       & 46.33          & 19.43         & 4/12          \\
+            Swahili(swa)           & \citep{wang2024multilingual}      + SVM                                & 29.52                        & 41.47                        & 22.65                       & 16/34         & —             & —           & —              & —             & —             & 29.52         & 38.43       & 33.27          & 18.99         & 5/15          \\
+            Swedish(swe)           & \citep{wang2024multilingual}     + SVM                                 & 56.51                        & 62.62                        & 51.98                       & 13/42         & —             & —           & —              & —             & —             & 56.51         & 64.53       & 51.18          & 51.18         & 6/14          \\
+            Tatar(tat)             & \citep{wang2024multilingual}    + SVM                                  & 64.32                        & 84.59                        & 53.94                       & 19/38         & —             & —           & —              & —             & —             & 64.32         & 83.59       & 60.66          & 44.54         & 5/12          \\
+            Tigrinya(tir)          & \citep{wang2024multilingual}    + SVM                                  & 52.37                        & 59.05                        & 46.28                       & 6/36          & —             & —           & —              & —             & —             & 52.37         & 55.24       & —              & 33.93         & 2/11          \\
+            Ukrainian(ukr)         & \citep{sturua2024jinaembeddingsv3multilingualembeddingstask}   + SVM   & 48.62                        & 72.56                        & 53.45                       & 31/42         & 42.55         & 70.75       & 43.54          & 39.94         & 17/25         & 48.62         & 71.99       & 54.76          & 49.56         & 11/18         \\
+            Emakhuwa(vmw)          & \citep{sturua2024jinaembeddingsv3multilingualembeddingstask}   + SVM   & 16.81                        & 32.50                        & 12.14                       & 15/33         & —             & —           & —              & —             & —             & 16.80         & 26.02       & 20.41          & 5.22          & 6/10          \\
+            isiXhosa(xho)          & \citep{wang2024multilingual}     + XGB                                 & —                            & —                            & —                           & —             & —             & —           & —              & —             & —             & 16.64         & 44.26       & 30.79          & 12.73         & 6/11          \\
+            Yoruba(yor)            & \citep{wang2024multilingual}     + SVM                                 & 34.09                        & 46.13                        & 9.22                        & 9/34          & —             & —           & —              & —             & —             & 34.09         & 46.79       & 27.44          & 5.33          & 4/12          \\
+            isiZulu(zul)           & \citep{wang2024multilingual}     + XGB                                 & —                            & —                            & —                           & —             & —             & —           & —              & —             & —             & 16.35         & 39.69       & 22.03          & 15.26         & 8/12          \\
+            \hline
+            % \\
+            % \bottomrule
+        \end{tabular}
+    }
+    \\
+    \footnotesize{\textit{BP*=result of rank 1\\BDP**=best result of dataset paper\citep{muhammad2025brighterbridginggaphumanannotated}\\pt***=Portuguese}}
+    \\
+    \footnotesize{The Best result of dataset paper for Track A is identical to that of Track C.}
+\end{table*}

### 2025-02-28 paper/sections/ExperimentalSetup.tex
add task paper citation

@@
 
-This section describes the experimental setup, providing details about data splits, preprocessing steps, hyperparameter tuning, computational resources, and the tools and libraries utilized.
-The goal is to ensure reproducibility, transparency, and alignment with established best practices in machine learning research.
+This section outlines the experimental setup, including data splits, preprocessing, hyperparameter tuning, computational resources, and the tools and libraries used, aiming for reproducibility and transparency.
+All experiments and evaluation protocols in this work are conducted following the guidelines specified in SemEval-2025 Task 11 \cite{muhammad-etal-2025-semeval}, which establishes the framework for text-based emotion detection.
+
 \begin{figure*}[t]

### 2025-04-09 paper/sections/Abstract.tex
final revision of paper

--- 2025-02-24 paper/sections/Abstract.tex
@@
 \begin{abstract}
-    This paper explores multilingual emotion classification across binary classification, intensity estimation, and cross-lingual detection tasks.
-To address linguistic variability and limited annotated data, we evaluate various deep learning approaches, including transformer-based embeddings and traditional classifiers.
-After extensive experimentation, language-specific embedding models were selected as the final approach, given their superior ability to capture linguistic and cultural nuances.
-Experiments on high- and low-resource languages demonstrate that this method significantly improves performance, achieving competitive macro-average F1 scores.
-Despite these advances, challenges remain due to limited annotated data in underrepresented languages and the complexity of nuanced emotional expressions.
-The study highlights the need for robust, language-aware emotion recognition systems and emphasizes future directions, including expanding multilingual datasets, refining models.
+    This paper investigates multilingual emotion classification across three tasks: binary classification, intensity estimation, and cross-lingual emotion detection.
+To address challenges posed by linguistic diversity and limited annotated data, we explore a range of deep learning approaches, including transformer-based embeddings and traditional classifiers.
+Following extensive experimentation, language-specific embedding models were selected as the final approach due to their superior capability to capture linguistic and cultural nuances.
+Evaluations on both high- and low-resource languages demonstrate that this method yields strong performance, achieving competitive macro-average F1 scores across tasks.
+Notably, in the cross-lingual detection task, our approach secured first-place rankings in Oromo, Tigrinya, and Kinyarwanda, driven by the integration of advanced preprocessing techniques and tailored language modeling.
+Despite these advances, challenges persist due to data scarcity in underrepresented languages and the inherent complexity of emotional expression.
+This study underscores the importance of developing robust, language-aware emotion recognition systems and highlights future directions, including the expansion of multilingual datasets and continued refinement of modeling techniques.
 \end{abstract}

### 2025-04-09 paper/tables/MainResults.tex
final revision of paper

--- 2025-02-23 paper/tables/MainResults.tex
@@
-% Multilingual-E5-large-instruct \citep{wang2024multilingual}
-% AraBert Large Algerian \citep{arabert}
+\begin{table*}[h]
+    \centering
+    \caption{Results across Track A, B, and C showing macro-average F1 scores of Our Model , Paraticipants Best Model scores, Task Dataset Best Model with Baseline\citep{muhammad2025brighterbridginggaphumanannotated} and rankings.}
+    \label{tab:results}
+    \resizebox{2\columnwidth}{!}{
+        \begin{tabular}{l|c|cccc|ccccc|ccccc}
+            \hline
+                                   &                                                                        & \multicolumn{4}{c|}{Track A} & \multicolumn{5}{c|}{Track B} & \multicolumn{5}{c}{Track C}                                                                                                                                                                                    \\
+            \cline{3-16}
+            \textbf{Language}      & \textbf{Our Model}                                                     & \textbf{Ours}                & \textbf{BP*}                 & \textbf{Base}               & \textbf{Rank} & \textbf{Ours} & \textbf{BP*} & \textbf{BDP**} & \textbf{Base} & \textbf{Rank} & \textbf{Ours}  & \textbf{BP*}   & \textbf{BDP**} & \textbf{Base} & \textbf{Rank} \\
+            \hline
+            Afrikaans(afr)         & \citep{wang2024multilingual} + SVM                                     & 54.01                        & 69.86                        & 37.14                       & 13/32         & —             & —            & —              & —             & —             & 54.01          & 70.50          & 61.28          & 35.04         & 4/12          \\
+            Amharic(amh)           & \citep{arabert}               + SVM                                    & 61.20                        & 77.31                        & 63.83                       & 18/40         & 49.42         & 85.58        & —              & 50.79         & 12/20         & 61.20          & 66.68          & —              & 48.66         & 4/11          \\
+            Algerian Arabic(arq)   & \citep{wang2024multilingual}   + SVM                                   & 51.07                        & 66.87                        & 41.41                       & 18/36         & 36.54         & 64.97        & 36.37          & 1.64          & 15/23         & 51.07          & 58.75          & 55.75          & 33.78         & 4/12          \\
+            Moroccan Arabic(ary)   & \citep{wang2024multilingual}   + SVM                                   & 51.88                        & 62.92                        & 47.16                       & 17/35         & —             & —            & —              & —             & —             & 51.88          & 63.22          & 52.76          & 35.46         & 4/10          \\
+            Chinese(chn)           & \citep{zpoint-large-embedding-zh} + SVM                                & 56.65                        & 70.94                        & 53.08                       & 25/36         & 48.47         & 72.24        & 51.86          & 40.53         & 15/24         & 56.65          & 68.89          & 55.23          & 24.56         & 5/12          \\
+            German(deu)            & \citep{wang2024multilingual}       + SVM                               & 60.60                        & 73.99                        & 64.23                       & 21/44         & 54.10         & 76.57        & 56.21          & 56.21         & 15/24         & 60.60          & 72.67          & 59.17          & 46.84         & 4/12          \\
+            English(eng)           & \citep{zhang2025jasperstelladistillationsota}  + SVM                   & 73.97                        & 82.30                        & 70.83                       & 28/74         & 68.81         & 84.04        & 64.15          & 64.15         & 20/36         & 73.97          & 79.69          & 65.58          & 37.54         & 3/12          \\
+            Spanish(esp)           & \citep{wang2024multilingual}      + SVM                                & 76.19                        & 84.88                        & 77.44                       & 24/44         & 66.70         & 80.80        & 72.59          & 72.59         & 20/26         & 76.19          & 83.11          & 73.29          & 57.37         & 3/13          \\
+            Hausa(hau)             & \citep{dobler-demelo-2023-focus} + SVM                                 & 63.22                        & 75.07                        & 59.55                       & 16/36         & 58.42         & 77.00        & 39.16          & 27.03         & 12/23         & 63.22          & 70.88          & 51.91          & 31.98         & \textbf{2/11} \\
+            Hindi(hin)             & \citep{wang2024multilingual}  + SVM                                    & 80.32                        & 92.57                        & 85.51                       & 30/39         & —             & —            & —              & —             & —             & 80.32          & 91.87          & 79.73          & 13.75         & 4/14          \\
+            Igbo(ibo)              & \citep{wang2024multilingual}   + SVM                                   & 50.93                        & 60.01                        & 47.90                       & 11/30         & —             & —            & —              & —             & —             & 50.93          & 60.47          & 37.40          & 7.49          & \textbf{2/9}  \\
+            Indonesian(ind)        & \citep{wang2024multilingual}   + XGB                                   & —                            & —                            & —                           & —             & —             & —            & —              & —             & —             & 35.64          & 67.24          & 57.29          & 37.64         & 13/15         \\
+            Javanese(jav)          & \citep{wang2024multilingual}   + XGB                                   & —                            & —                            & —                           & —             & —             & —            & —              & —             & —             & 25.62          & 46.38          & 50.47          & 46.38         & 10/11         \\
+            Kinyarwanda(kin)       & \citep{wang2024multilingual}  + SVM                                    & 51.94                        & 65.74                        & 46.29                       & 5/28          & —             & —            & —              & —             & —             & \textbf{51.94} & \textbf{51.94} & 34.36          & 18.38         & \textbf{1/8}  \\
+            Marathi(mar)           & \citep{wang2024multilingual}   + SVM                                   & 81.10                        & 88.43                        & 82.20                       & 21/37         & —             & —            & —              & —             & —             & 81.10          & 90.29          & 77.24          & 77.24         & 4/11          \\
+            Oromo(orm)             & \citep{wang2024multilingual}    + SVM                                  & 54.31                        & 61.64                        & 12.63                       & 9/31          & —             & —            & —              & —             & —             & \textbf{54.31} & \textbf{54.31} & —              & 26.17         & \textbf{1/9}  \\
+            Nigerian-Pidgin(pcm)   & \citep{wang2024multilingual}   + SVM                                   & 53.09                        & 67.40                        & 55.50                       & 19/30         & —             & —            & —              & —             & —             & 53.09          & 67.40          & 48.67          & 1.01          & 3/8           \\
+            Pt*** Brazilian(ptbr)  & \citep{souza2020bertimbau} + SVM                                       & 47.99                        & 68.33                        & 42.57                       & 23/37         & 38.20         & 71.00        & 46.72          & 29.74         & 19/23         & 47.99          & 62.91          & 51.60          & 41.84         & 5/11          \\
+            Pt*** Mozambican(ptmz) & \citep{wang2024multilingual}   + SVM                                   & 50.08                        & 54.77                        & 45.91                       & 5/32          & —             & —            & —              & —             & —             & 50.08          & 55.54          & 40.44          & 29.67         & \textbf{2/11} \\
+            Romanian(ron)          & \citep{wang2024multilingual}     + SVM                                 & 73.75                        & 79.43                        & 76.23                       & 14/39         & 57.61         & 72.60        & 57.69          & 55.66         & 14/22         & 73.75          & 76.70          & 76.23          & 76.23         & 4/13          \\
+            Russian(rus)           & \citep{snegirev2025russianfocusedembeddersexplorationrumteb}     + SVM & 82.42                        & 90.08                        & 83.77                       & 28/44         & 78.41         & 92.54        & 87.66          & 87.66         & 18/25         & 82.42          & 90.58          & 76.97          & 70.43         & 4/14          \\
+            Somali(som)            & \citep{wang2024multilingual}       + SVM                               & 48.26                        & 57.65                        & 45.93                       & 7/29          & —             & —            & —              & —             & —             & 48.26          & 47.79          & —              & 27.27         & 3/10          \\
+            Sundanese(sun)         & \citep{wang2024multilingual}      + SVM                                & 42.48                        & 54.97                        & 37.31                       & 17/32         & —             & —            & —              & —             & —             & 42.48          & 46.66          & 46.33          & 19.43         & 3/9           \\
+            Swahili(swa)           & \citep{wang2024multilingual}      + SVM                                & 29.52                        & 38.56                        & 22.65                       & 13/29         & —             & —            & —              & —             & —             & 29.52          & 38.05          & 33.27          & 18.99         & 3/11          \\
+            Swedish(swe)           & \citep{wang2024multilingual}     + SVM                                 & 56.51                        & 62.62                        & 51.98                       & 12/34         & —             & —            & —              & —             & —             & 56.51          & 64.53          & 51.18          & 51.18         & 4/11          \\
+            Tatar(tat)             & \citep{wang2024multilingual}    + SVM                                  & 64.32                        & 84.59                        & 53.94                       & 15/31         & —             & —            & —              & —             & —             & 64.32          & 78.86          & 60.66          & 44.54         & 3/9           \\
+            Tigrinya(tir)          & \citep{wang2024multilingual}    + SVM                                  & 52.37                        & 59.05                        & 46.28                       & 6/28          & —             & —            & —              & —             & —             & \textbf{52.37} & \textbf{52.37} & —              & 33.93         & \textbf{1/8}  \\
+            Ukrainian(ukr)         & \citep{sturua2024jinaembeddingsv3multilingualembeddingstask}   + SVM   & 48.62                        & 72.56                        & 53.45                       & 26/36         & 42.55         & 70.75        & 43.54          & 39.94         & 13/21         & 48.62          & 70.18          & 54.76          & 49.56         & 9/15          \\
+            Emakhuwa(vmw)          & \citep{sturua2024jinaembeddingsv3multilingualembeddingstask}   + SVM   & 16.81                        & 32.50                        & 12.14                       & 11/20         & —             & —            & —              & —             & —             & 16.80          & 21.04          & 20.41          & 5.22          & 4/7           \\
+            isiXhosa(xho)          & \citep{wang2024multilingual}     + XGB                                 & —                            & —                            & —                           & —             & —             & —            & —              & —             & —             & 16.64          & 44.26          & 30.79          & 12.73         & 4/8           \\
+            Yoruba(yor)            & \citep{wang2024multilingual}     + SVM                                 & 34.09                        & 46.13                        & 9.22                        & 7/30          & —             & —            & —              & —             & —             & 34.09          & 35.95          & 27.44          & 5.33          & 3/8           \\
+            isiZulu(zul)           & \citep{wang2024multilingual}     + XGB                                 & —                            & —                            & —                           & —             & —             & —            & —              & —             & —             & 16.35          & 39.69          & 22.03          & 15.26         & 6/9           \\
+            \hline
+            % \\
+            % \bottomrule
+        \end{tabular}
+    }
+    \\
+    \footnotesize{\textit{BP*=result of rank 1\\BDP**=best result of dataset paper\citep{muhammad2025brighterbridginggaphumanannotated}\\pt***=Portuguese}}
+    \\
+    \footnotesize{The Best result of dataset paper for Track A is identical to that of Track C.}
+\end{table*}

### 2025-05-11 paper/sections/introduction.tex
fix github link

@@
 
-All code implementations, including the models and experimental setups employed in this study, are publicly available on GitHub:\footnote{\url{https://github.com/YNWA-PZ/SemEval2025-task11}}.
+All code implementations, including the models and experimental setups employed in this study, are publicly available on GitHub:\footnote{\href{https://github.com/YNWA-PZ/SemEval2025-task11}{https://github.com/YNWA-PZ/SemEval2025-task11}}.
 This repository provides full documentation of our methodologies, experimental results, and final model architectures.
